\documentstyle{article}
\begin{document}

%%% PUBLICATIONS on IDENTIFYING AND LOCATING-DOMINATING CODES
%%% + DISCRIMINATING and around
%%% (dominating, locating, locating-chromatic number,
%%% metric-locating-dominating, complexity,
%%% well-covered graphs, ...)
%%%
%%%   ALPHABETICAL ORDER
%%%
%%%   CHECK:
%%%   names,
%%%   << & >> vs. << and >>,
%%%   month in English,
%%%   << , >> vs. << : >> after authors,
%%%   << , >> vs. << . >> after titles,
%%%   capitals in titles,
%%%   << vol. >> vs. << Vol. >>,
%%%   Proceedings, ...
%%%   http://

\begin{center}
\textit{In Memoriam} \\
\vspace{1em}
\textbf{G\'erard COHEN} \\
\textbf{Fr\'ed\'eric MAFFRAY} \\
\textbf{Yannis MANOUSSAKIS} \\
\textbf{Peter SLATER}
\end{center}

\bigskip
\noindent \fbox{\parbox{\linewidth \fboxrule \fboxsep}{
\noindent \textbf{\underline{New Maintainer}}
\medskip \\
\noindent I am Devin Jean, and I will be continuing to maintain this bibliography for the foreseeable future.
If you would like to recommend a new publication be added, feel free to contact me at \texttt{devin.c.jean@vanderbilt.edu}.
I will try to stay up to date with new publications, but emails from authors would be greatly appreciated.
}}
\bigskip

\begin{center}
\noindent \textbf{SYST\`EMES DE CONTR\^OLE,\\CODES IDENTIFIANTS, LOCALISATEURS-DOMINATEURS ET DISCRIMINANTS DANS LES GRAPHES}\\
\bigskip
\noindent \textbf{WATCHING SYSTEMS,\\IDENTIFYING, LOCATING-DOMINATING\\AND DISCRIMINATING CODES IN GRAPHS} \\
\bigskip
\today
\end{center}

\begin{thebibliography}{999}

\bibitem{abdu21k}
A. K. ABDUL~GAFUR and S. W. SAPUTRO: On locating-dominating set of regular graphs, {\it Journal of Mathematics}, Paper ID 8147514, 6 pages, 2021.

\bibitem{ahma21}
E. C. AHMAD, G. A. MALACAS and S. R. CANOY, Jr.: Stable locating-dominating sets in graphs, {\it European Journal of Pure and Applied Mathematics}, Vol. 14(3), pp. 638--649, 2021.

\bibitem{aide16}
M. A\"IDER, S. GRAVIER and S. SLIMANI: Relaxed locally identifying coloring of graphs, {\it Graphs and Combinatorics}, Vol.~32(5), pp. 1651--1665, 2016.

\bibitem{ange21}
D. ANGEL, I. A. ARPUTHAMARY and K. EZHILARASI: Location domination for generalized friendship graphs analytics, {\it Proceedings of 2021 5th International Conference on Computing Methodologies and Communication (ICCMC)}, pp. 865--868, 2021.

\bibitem{arau11}
G. ARAUJO-PARDO, C. BALBUENA, L. MONTEJANO and J. C. VALENZUELA: Partial linear spaces and identifying codes, {\it European Journal of Combinatorics}, Vol.~32, pp. 344--351, 2011.

\bibitem{argi17}
G. R. ARGIROFFO, S. M. BIANCHI, Y. P. LUCARINI and A. K. WAGLER: A linear-time algorithm for the identifying code problem on block graphs, {\it Electronic Notes in Discrete Mathematics}, Vol.~62, pp. 249--254, 2017.

\bibitem{argi18}
G. R. ARGIROFFO, S. M. BIANCHI, Y. P. LUCARINI and A. K. WAGLER: Polyhedra associated with identifying codes in graphs, {\it Discrete Applied Mathematics}, Vol. 245, pp. 16--27, 2018.

\bibitem{argi19L}
G. R. ARGIROFFO, S. M. BIANCHI, Y. P. LUCARINI and A. K. WAGLER: The identifying code, the locating-dominating, the open locating-dominating and the locating total-dominating problems under some graph operations, {\it Electronic Notes in Theoretical Computer Science}, Vol. 346, pp. 135--145, 2019.

\bibitem{argi20k}
G. R. ARGIROFFO, S. M. BIANCHI, Y. P. LUCARINI and A. K. WAGLER: Polyhedra associated with open locating-dominating and locating total-dominating sets in graphs, {\it Lecture Notes in Computer Science}, No. 12176, pp. 3--14, Springer, 2020.

\bibitem{argi20q}
G. R. ARGIROFFO, S. M. BIANCHI, Y. P. LUCARINI and A. K. WAGLER: Linear-time algorithms for three domination-based separation problems in block graphs, {\it Discrete Applied Mathematics}, Vol. 281, pp. 6--41, 2020.

\bibitem{argi22L}
G. R. ARGIROFFO, S. M. BIANCHI, Y. P. LUCARINI and A. K. WAGLER: Polyhedra associated with locating-dominating, open locating-dominating and locating total-dominating sets in graphs, {\it Discrete Applied Mathematics}, Vol. 322, pp. 465--480, 2022.

\bibitem{argi13}
G. R. ARGIROFFO, S. M. BIANCHI and A. K. WAGLER: Polyhedra associated to identifying codes, {\it Electronic Notes in Discrete Mathematics}, Vol.~44, pp. 175--180, 2013.

\bibitem{argi14}
G. R. ARGIROFFO, S. M. BIANCHI and A. K. WAGLER: Study of identifying code polyhedra for some families of split graphs, {\it Lecture Notes in Computer Science}, No. 8596, pp. 13--25, Springer-Verlag, 2014.

\bibitem{argi14a}
G. R. ARGIROFFO, S. M. BIANCHI and A. K. WAGLER: On identifying code polyhedra of families of suns, {\it Proceedings of VIII-th ALIO/EURO Workshop on Applied Combinatorial Optimization}, Montevideo, Uruguay, December 2014.

\bibitem{argi15}
G. R. ARGIROFFO, S. M. BIANCHI and A. K. WAGLER: A polyhedral approach to locating-dominating sets in graphs, {\it Electronic Notes in Discrete Mathematics}, Vol.~50, pp. 89--94, 2015.

\bibitem{argi16}
G. R. ARGIROFFO, S. M. BIANCHI and A. K. WAGLER: Progress on the description of identifying code polyhedra for some families of split graphs, {\it Discrete Optimization}, Vol.~22, pp. 225--240,  2016.

\bibitem{assi11}
A. H. ASSIYATUN and E. T. BASKORO: Locating-chromatic number of amalgamation of stars, {\it Institut Teknologi Bandung Journal of Science}, Vol.~43A, pp. 1--8, 2011.

\bibitem{auge07}
D. AUGER: Probl\`emes d'identification m\'etrique dans les graphes, {\it Rapport interne T\'el\'ecom Paris-2007D013}, Paris, France, 44 pages, 2007.

\bibitem{auge09a}
D. AUGER: Induced paths in twin-free graphs, {\it Electronic Journal of Combinatorics}, Vol.~15(1), N17, 2008.\\
http://www.combinatorics.org

\bibitem{auge09e}
D. AUGER: Identifying codes in trees and planar graphs, {\it Electronic Notes in Discrete Mathematics}, Vol.~34, pp. 585--588, 2009.

\bibitem{auge09f}
D. AUGER: Minimal identifying codes in trees and planar graphs with large girth, {\it European Journal of Combinatorics}, Vol.~31, pp. 1372--1384, 2010.

\bibitem{auge10a}
D. AUGER: Probl\`emes d'identification combinatoire et puissances de graphes, {\it Th\`ese de Doctorat}, Telecom ParisTech, France, 243 pages, June 2010.

\bibitem{auge11}
D. AUGER: Combinatorial identification problems and graph powers, {\it 4OR: A Quaterly Journal of Operations Research}, Vol.~9, pp. 417--420, 2011.

\bibitem{auge09b}
D. AUGER, I. CHARON, I. HONKALA, O. HUDRY and A. LOBSTEIN: Edge number, minimum degree, maximum independent set, radius and diameter in twin-free graphs, {\it Advances in Mathematics of Communications}, Vol.~3(1), pp. 97--114, 2009. Erratum in Vol.~3(4), pp. 429--430, 2009.

\bibitem{auge09d}
D. AUGER, I. CHARON, O. HUDRY and A. LOBSTEIN: Existence d'un cycle de longueur au moins~$7$ dans un graphe sans ($1,\leq 2$)-jumeaux, {\it Rapport interne Telecom ParisTech-2009D015}, Paris, France, 18 pages, 2009.

\bibitem{auge10}
D. AUGER, I. CHARON, O. HUDRY and A. LOBSTEIN: Maximum size of a minimum watching system and the graphs achieving the bound, {\it Rapport interne Telecom ParisTech-2010D011}, Paris, France, 40 pages, 2010.

\bibitem{auge09g}
D. AUGER, I. CHARON, O. HUDRY and A. LOBSTEIN: On the existence of a cycle of length at least~7 in a $(1,\leq 2)$-twin-free graph, {\it Discussiones Mathematicae Graph Theory}, Vol.~30, pp. 591--609, 2010.

\bibitem{auge09c}
D. AUGER, I. CHARON, O. HUDRY and A. LOBSTEIN: Complexity results for identifying codes in planar graphs, {\it International Transactions in Operational Research}, Vol.~17, pp. 691--710, 2010.

\bibitem{auge09h}
D. AUGER, I. CHARON, O. HUDRY and A. LOBSTEIN: Watching systems in graphs: an extension of identifying codes, {\it Discrete Applied Mathematics}, Vol.~161, pp. 1674--1685, 2013.

\bibitem{auge12a}
D. AUGER, I. CHARON, O. HUDRY and A. LOBSTEIN: Maximum size of a minimum watching system and the graphs achieving the bound, {\it Discrete Applied Mathematics}, Vol.~164, pp. 20--33, 2014.

\bibitem{auge11b}
D. AUGER, G. COHEN and S. MESNAGER: Sphere coverings and identifying codes, {\it Designs, Codes and Cryptography}, Vol.~70, pp. 3--7, 2014.

\bibitem{auge12}
D. AUGER and I. HONKALA: Watching systems in the king grid, {\it Graphs and Combinatorics}, Vol.~29, pp. 333--347, 2013.

\bibitem{baba80}
L. BABAI: On the complexity of canonical labeling of strong regular graphs, {\it SIAM Journal of Computing}, Vol.~9, pp. 212--216, 1980.

\bibitem{balb19}
C. BALBUENA, C. DALF\'O and B. MART\'INEZ-BARONA: Characterizing identifying codes from the spectrum of a graph or digraph, {\it Linear Algebra and its Applications}, Vol. 570, pp. 138--147, 2019.

\bibitem{balb20k}
C. BALBUENA, C. DALF\'O and B. MART\'INEZ-BARONA: Identifying codes in line digraphs, {\it Applied Mathematics and Computation}, Vol. 383, 125357, 10 pages, 2020.

\bibitem{balb20q}
C. BALBUENA, C. DALF\'O and B. MART\'INEZ-BARONA: Sufficient conditions for a digraph to admit a (1,$\leq \ell$)-identifying code, {\it Discussiones Mathematicae Graph Theory}, Vol. 41(4), pp. 853--872, 2021.

\bibitem{balb15}
C. BALBUENA, F. FOUCAUD and A. HANSBERG: Locating-dominating sets and identifying codes in graphs of girth at least~5, {\it Electronic Journal of Combinatorics}, Vol.~22(2), P2.15, 22 pages, 2015.\\
http://www.combinatorics.org

\bibitem{barb19k}
F. BARBERO, L. ISENMANN and J. THIEBAUT: On the distance identifying set meta-problem and applications to the complexity of identifying problems on graphs, {\it Proceedings of 13th International Symposium on Parameterized and Exact Computation}, Leibniz International Proceedings in Informatics, Vol. 115, Paper 10, 14 pages, 2019.

\bibitem{barb20k}
F. BARBERO, L. ISENMANN and J. THIEBAUT: On the Distance Identifying Set meta-problem and applications to the complexity of identifying problems on graphs, {\it Algorithmica}, Vol. 82(8), pp. 2243--2266, 2020.

\bibitem{bask21}
E. T. BASKORO and D. I. D. PRIMASKUN: Improved algorithm for the locating-chromatic number of trees, {\it Theoretical Computer Science}, Vol. 856, pp. 165--168, 2021.

\bibitem{basuC21}
K. BASU and A. SEN: Identifying individuals associated with organized criminal networks: A social network analysis, {\it Social Networks}, Vol. 64, pp. 42--54, 2021.

\bibitem{beau18}
L. BEAUDOU, P. DANKELMANN, F. FOUCAUD, M. A. HENNING, A. MARY and A. PARREAU: Bounding the order of a graph using its diameter and metric dimension: a study through tree decompositions and VC dimension, {\it SIAM Journal on Discrete Mathematics}, Vol.~32(2), pp. 902--918, 2018.

\bibitem{beht14}
A. BEHTOEI and M. ANBARLOEI: The locating chromatic number of the join of graphs, {\it Bulletin of the Iranian Mathematical Society}, Vol.~40(6), pp. 1491--1504, 2014.

\bibitem{beht15}
A. BEHTOEI and M. ANBARLOEI: A bound for the locating chromatic number of trees, {\it Transactions on Combinatorics}, Vol.~4(1), pp. 31--41, 2015.

\bibitem{beht11}
A. BEHTOEI and B. OMOOMI: On the locating chromatic number of Kneser graphs, {\it Discrete Applied Mathematics}, Vol.~159, pp. 2214--2221, 2011.

\bibitem{beht16}
A. BEHTOEI and B. OMOOMI: On the locating chromatic number of the Cartesian product of graphs, {\it Ars Combinatoria}, Vol. 126, pp. 221--235, 2016.

\bibitem{benh08a}
Y. BEN-HAIM, S. GRAVIER, A. LOBSTEIN and J. MONCEL: Adaptive identification in graphs, {\it Rapport interne T\'el\'ecom Paris-2007D012}, Paris, France, 33 pages, September 2007.

\bibitem{benh08}
Y. BEN-HAIM, S. GRAVIER, A. LOBSTEIN and J. MONCEL: Adaptive identification in graphs, {\it Journal of Combinatorial Theory}, Ser. A, Vol.~115, pp. 1114--1126, 2008.

\bibitem{benh09}
Y. BEN-HAIM, S. GRAVIER, A. LOBSTEIN and J. MONCEL: Adaptive identification in torii in the king lattice, {\it Electronic Journal of Combinatorics}, Vol.~18(1), P116, 2011.\\
http://www.combinatorics.org

\bibitem{lits04}
Y. BEN-HAIM and S. LITSYN: Exact minimum density of codes identifying vertices in the square grid, {\it SIAM Journal on Discrete Mathematics}, Vol.~19, pp. 69--82, 2005.

\bibitem{bens18}
J. BENSMAIL, D. MAZAURIC, F. MC~INERNEY, N. NISSE and S. P\'E\-RENNES: Sequential metric dimension, {\it Lecture Notes in Computer Science}, No. 11312, pp. 36--50, Springer-Verlag, 2018.

\bibitem{berg05}
T. Y. BERGER-WOLF, W. E. HART and J. SAIA: Discrete sensor placement problems in distribution networks, {\it Mathematical and Computer Modelling}, Vol.~42, pp. 1385--1396, 2005.

\bibitem{berg06}
T. Y. BERGER-WOLF, M. LAIFENFELD and A. TRACHTENBERG: Identifying codes and the set cover problem, {\it Proceedings of the 44th Annual Allerton Conference on Communication, Control and Computing}, Monticello, USA, September 2006.

\bibitem{bert01}
N. BERTRAND: Codes identifiants et codes localisateurs-dominateurs sur certains graphes, {\it M\'emoire de stage de ma\^{\i}trise}, ENST, Paris, France, 28 pages, June 2001.

\bibitem{bert03a}
N. BERTRAND, I. CHARON, O. HUDRY and A. LOBSTEIN: Identifying or locating-dominating codes for some families of graphs, {\it Rapport interne T\'el\'ecom Paris-2003C001}, Paris, France, 48 pages, February 2003.

\bibitem{bert03c}
N. BERTRAND, I. CHARON, O. HUDRY and A. LOBSTEIN: Identifying and locating-dominating codes on chains and cycles, {\it European Journal of Combinatorics}, Vol.~25, pp. 969--987, 2004.

\bibitem{bert03b}
N. BERTRAND, I. CHARON, O. HUDRY and A. LOBSTEIN: 1-identifying codes on trees, {\it Australasian Journal of Combinatorics}, Vol.~31, pp. 21--35, 2005.

\bibitem{blas99a}
U. BLASS, I. HONKALA and S. LITSYN: On the size of identifying codes, {\it Lecture Notes in Computer Science}, No. 1719, pp. 142--147, Springer-Verlag, 1999.

\bibitem{blas00a}
U. BLASS, I. HONKALA and S. LITSYN: On binary codes for identification, {\it Journal of Combinatorial Designs}, Vol.~8, pp. 151--156, 2000.

\bibitem{blas01a}
U. BLASS, I. HONKALA and S. LITSYN: Bounds on identifying codes, {\it Discrete Mathematics}, Vol.~241, pp. 119--128, 2001.

\bibitem{blidC18}
M. BLIDIA and M. CHELLALI: Locating domination dot-critical graphs, {\it Journal of Combinatorial Mathematics and Combinatorial Computing}, Vol. 104, pp. 121--141, 2018.

\bibitem{blid11}
M. BLIDIA, M. CHELLALI, R. LOUNES and F. MAFFRAY: Characterizations of trees with unique minimum locating-dominating sets, {\it Journal of Combinatorial Mathematics and Combinatorial Computing}, Vol.~76, pp. 225--232, 2011.

\bibitem{blid07}
M. BLIDIA, M. CHELLALI, F. MAFFRAY, J. MONCEL and A. SEMRI: Locating-domination and identifying codes in trees, {\it Australasian Journal of Combinatorics}, Vol.~39, pp. 219--232, 2007.

\bibitem{blid09b}
M. BLIDIA and W. DALI: A characterization of locating-domination edge critical graphs, {\it Australasian Journal of Combinatorics}, Vol.~44, pp. 297--300, 2009.

\bibitem{blid11k}
M. BLIDIA and W. DALI: A characterization of locating-total domination edge critical graphs, {\it Discussiones Mathematicae Graph Theory}, Vol.~31, pp. 197--202, 2011.

\bibitem{blidC14}
M. BLIDIA and W. DALI: On locating and locating-total domination edge addition critical graphs, {\it Utilitas Mathematica}, Vol. 94, pp. 303--313, 2014.

\bibitem{blid08}
M. BLIDIA, O. FAVARON and R. LOUNES: Locating-domination, 2-domination and independence in trees, {\it Australasian Journal of Combinatorics}, Vol.~42, pp. 309--316, 2008.

\bibitem{blid09}
M. BLIDIA and R. LOUNES: Vertices belonging to all or to no minimum locating dominating sets of trees, {\it Opuscula Mathematica}, Vol.~29, pp. 5--14, 2009.

\bibitem{bous23}
N. BOUSQUET, Q. DESCHAMPS, T. LEHTIL\"A and A. PARREAU: Locating-dominating sets: {F}rom graphs to oriented graphs, {\it Discrete Mathematics}, Vol. 346(1), 113124, 2023.

\bibitem{bous14}
N. BOUSQUET, A. LAGOUTTE, Z. LI, A. PARREAU and S. THO\-MASS\'E: Identifying codes and VC-dimension, {\it Proceedings of Bordeaux Graph Workshop}, Bordeaux, France, pp. 63--64, 2014.

\bibitem{bous15}
N. BOUSQUET, A. LAGOUTTE, Z. LI, A. PARREAU and S. THO\-MASS\'E: Identifying codes in hereditary classes of graphs and VC-dimension, {\it SIAM Journal on Discrete Mathematics}, Vol.~29(4), pp. 2047--2064, 2015.

\bibitem{bout19}
D. BOUTIN, V. H. GOLIBER and M. PELTO: Identifying codes on directed de Bruijn graphs, {\it Discrete Applied Mathematics}, Vol. 262, pp. 29--41, 2019.

\bibitem{bouz12}
M. BOUZNIF: Algorithmes g\'en\'eriques en temps constant pour la r\'eso\-lution de probl\`emes combinatoires dans la classe des rotagraphes et fasciagraphes. Application aux codes identifiants, dominant-localisateurs et total-dominant-localisateurs, {\it Th\`ese de Doctorat}, Universit\'e de Grenoble, France, 131 pages, July 2012.

\bibitem{bouz19k}
M. BOUZNIF, J. DARLAY, J. MONCEL and M. PREISSMANN: Exact values for three domination-like problems in circular and infinite grid graphs of small height, {\it Discrete Mathematics \& Theoretical Computer Science}, Vol. 21(3), Paper No. 12, 21 pages, 2019.

\bibitem{bouz16}
M. BOUZNIF, F. HAVET and M. PREISSMANN: Minimum-density identifying codes in square grids, {\it Lecture Notes in Computer Science}, No.~9778, pp. 77--88, Springer-Verlag, 2016.

\bibitem{bouz12a}
M. BOUZNIF, J. MONCEL and M. PREISSMANN: Generic algorithms for some decision problems on fasciagraphs and rotagraphs, {\it Discrete Mathematics}, Vol.~312, pp. 2707--2719, 2012.

\bibitem{cace10}
J. C\'ACERES, D. GARIJO, M. L. PUERTAS and C. SEARA: On the determining number and the metric dimension of graphs, {\it Electronic Journal of Combinatorics}, Vol.~17(1), R63, 2010.\\
http://www.combinatorics.org

\bibitem{cace12}
J. C\'ACERES, C. HERNANDO, M. MORA, I. M. PELAYO and M. L. PUERTAS: Locating-dominating codes: Bounds and extremal cardinalities, {\it Applied Mathematics and Computation}, Vol.~220, pp. 38--45, 2013.

\bibitem{cace07}
J. C\'ACERES, C. HERNANDO, M. MORA, I. M. PELAYO, M. L. PUERTAS, C. SEARA and D. R. WOOD: On the metric dimension of Cartesian products of graphs, {\it SIAM Journal on Discrete Mathematics}, Vol.~21(2), pp. 423--441, 2007.

\bibitem{cama15}
C. CAMARERO, C. MARTINEZ and R. BEIVIDE: Identifying codes of degree~$4$ Cayley graphs over Abelian groups, {\it Advances in Mathematics of Communications}, Vol.~9, pp. 129--148, 2015.

\bibitem{cano13}
S. R. CANOY, Jr. and G. A. MALACAS: Determining the intruders location in a given network: Locating-dominating sets in a graph, {\it NCRP Research Journal}, Vol.~13(1), pp. 1--8, 2013.

\bibitem{cano15}
S. R. CANOY, Jr. and G. A. MALACAS: Differentiating-dominating sets in graphs under binary operations, {\it Tamkang Journal of Mathematics}, Vol.~46, pp. 51--60, 2015.

\bibitem{cano22C}
S. R. CANOY, Jr. and G. P. SALASALAN: Locating-hop domination in graphs, {\it Kyungpook Mathematical Journal}, Vol. 62, pp. 193--204, 2022.

\bibitem{cape19}
M. R. CAPPELLE, E. M. COELHO, L. R. FOULDS and H. J. LONGO: Open-independent, open-locating-dominating sets in complementary prism graphs, {\it Electronic Notes in Theoretical Computer Science}, Vol. 346, pp. 253--264, 2019.

\bibitem{capp22C}
M. R. CAPPELLE, E. M. M. COELHO, L. R. FOULDS and H. J. LONGO: Complexity results on open-independent, open-locating-dominating sets in complementary prism graphs, {\it Discrete Applied Mathematics}, Vol. 323, pp. 124--133, 2022.

\bibitem{capp22K}
M. R. CAPPELLE, E. M. M. COELHO, L. R. FOULDS and H. J. LONGO: Open-independent, open-locating-dominating sets: structural aspects of some classes of graphs, {\it Discrete Mathematics \& Theoretical Computer Science}, Vol. 24(1), Paper No. 5, 18 pages, 2022.

\bibitem{cars95a}
D. I. CARSON: On generalized location-domination, {\it Graph Theory, Combinatorics, and Applications: Proceedings of the 7th Quadrennial International Conference on the Theory and Applications of Graphs}, Vol.~1, pp. 161--179, Wiley, 1995.

\bibitem{chak98a}
K. CHAKRABARTY, M. G. KARPOVSKY and L. B. LEVITIN: Fault detection and diagnosis in multiprocessor systems with point-to-point connections, {\it Fault Tolerant Parallel and Distributed Systems}, pp. 285--301, Kluwer, 1998.

\bibitem{chan14}
T. P. CHANG and L. D. TONG: Choice identification of a graph, {\it Discrete Applied Mathematics}, Vol.~167, pp. 61--71, 2014.

\bibitem{Echa06}
E. CHARBIT, I. CHARON, G. COHEN and O. HUDRY: Discriminating codes in bipartite graphs, {\it Electronic Notes in Discrete Mathematics}, Vol.~26, pp. 29--35, 2006.

\bibitem{Echa09}
E. CHARBIT, I. CHARON, G. COHEN, O. HUDRY and A. LOBSTEIN: Discriminating codes in bipartite graphs: bounds, extremal cardinalities, complexity, {\it Advances in Mathematics of Communications}, Vol.~4(2), pp. 403--420, 2008.

\bibitem{char08c}
I. CHARON, G. COHEN, O. HUDRY and A. LOBSTEIN: Links between discriminating and identifying codes in the binary Hamming space, {\it Lecture Notes in Computer Science}, No.~4851, pp. 267--270, Springer-Verlag, 2007.

\bibitem{char08}
I. CHARON, G. COHEN, O. HUDRY and A. LOBSTEIN: Discriminating codes in (bipartite) planar graphs, {\it European Journal of Combinatorics}, Vol.~29, pp. 1353--1364, 2008.

\bibitem{char08b}
I. CHARON, G. COHEN, O. HUDRY and A. LOBSTEIN: New identifying codes in the binary Hamming space, {\it European Journal of Combinatorics}, Vol.~31, pp. 491--501, 2010.

\bibitem{char05}
I. CHARON, S. GRAVIER, O. HUDRY, A. LOBSTEIN, M. MOLLARD and J. MONCEL: A linear algorithm for minimum 1-identifying codes in oriented trees, {\it Discrete Applied Mathematics}, Vol.~154, pp. 1246--1253, 2006.

\bibitem{char00a}
I. CHARON, I. HONKALA, O. HUDRY and A. LOBSTEIN: Identifying codes, {\it Rapport interne T\'el\'ecom Paris-2000D009}, Paris, France, 67 pages, October 2000.

\bibitem{char01a}
I. CHARON, I. HONKALA, O. HUDRY and A. LOBSTEIN: General bounds for identifying codes in some infinite regular graphs, {\it Electronic Journal of Combinatorics}, Vol.~8(1), R39, 2001.\\
http://www.combinatorics.org

\bibitem{char03a}
I. CHARON, I. HONKALA, O. HUDRY and A. LOBSTEIN: The minimum density of an identifying code in the king lattice, {\it Discrete Mathematics}, Vol.~276, pp. 95--109, 2004.

\bibitem{char06}
I. CHARON, I. HONKALA, O. HUDRY and A. LOBSTEIN: Structural properties of twin-free graphs, {\it Electronic Journal of Combinatorics}, Vol.~14(1), R16, 2007.\\
http://www.combinatorics.org

\bibitem{char12b}
I. CHARON, I. HONKALA, O. HUDRY and A. LOBSTEIN: Minimum sizes of identifying codes in graphs differing by one vertex, {\it Cryptography and Communications -- Discrete Structures, Boolean Functions and Sequences}, Vol.~5, pp. 119--136, 2013.

\bibitem{char12a}
I. CHARON, I. HONKALA, O. HUDRY and A. LOBSTEIN: Minimum sizes of identifying codes in graphs differing by one edge, {\it Cryptography and Communications -- Discrete Structures, Boolean Functions and Sequences}, Vol.~6, pp. 157--170, 2014.

\bibitem{char01b}
I. CHARON, O. HUDRY and A. LOBSTEIN: Complexity of identifying and locating problems in graphs, {\it Rapport interne T\'el\'ecom Paris-2001D013}, Paris, France, 36 pages, October 2001.

\bibitem{char02a}
I. CHARON, O. HUDRY and A. LOBSTEIN: Identifying codes with small radius in some infinite regular graphs, {\it Electronic Journal of Combinatorics}, Vol.~9(1), R11, 2002.\\
http://www.combinatorics.org

\bibitem{char02b}
I. CHARON, O. HUDRY and A. LOBSTEIN: Identifying and locating-dominating codes: NP-completeness results for directed graphs, {\it IEEE Transactions on Information Theory}, Vol. IT-48, pp. 2192--2200, 2002.

\bibitem{char03b}
I. CHARON, O. HUDRY and A. LOBSTEIN: Minimizing the size of an identifying or locating-dominating code in a graph is NP-hard, {\it Theoretical Computer Science}, Vol.~290, pp. 2109--2120, 2003.

\bibitem{char03c}
I. CHARON, O. HUDRY and A. LOBSTEIN: Extremal cardinalities for identifying and locating-dominating codes in graphs, {\it Rapport interne T\'el\'ecom Paris-2003D006}, Paris, France, 18 pages, August 2003.

\bibitem{char04a}
I. CHARON, O. HUDRY and A. LOBSTEIN: Possible cardinalities for identifying codes in graphs, {\it Australasian Journal of Combinatorics}, Vol.~32, pp. 177--195, 2005.

\bibitem{char05a}
I. CHARON, O. HUDRY and A. LOBSTEIN: On the structure of identifiable graphs, {\it Electronic Notes in Discrete Mathematics}, Vol.~22, pp. 491--495, 2005.

\bibitem{char04c}
I. CHARON, O. HUDRY and A. LOBSTEIN: Possible cardinalities for locating-dominating codes in graphs, {\it Australasian Journal of Combinatorics}, Vol.~34, pp. 23--32, 2006.

\bibitem{char04b}
I. CHARON, O. HUDRY and A. LOBSTEIN: Extremal cardinalities for identifying and locating-dominating codes in graphs, {\it Discrete Mathematics}, Vol.~307, pp. 356--366, 2007.

\bibitem{char08a}
I. CHARON, O. HUDRY and A. LOBSTEIN: Extremal values for the maximum degree in a twin-free graph, {\it Rapport interne TELECOM ParisTech-2008D007}, Paris, France, 17 pages, May 2008.

\bibitem{char07}
I. CHARON, O. HUDRY and A. LOBSTEIN: Extremal values for identification, domination and maximum cliques in twin-free graphs, {\it Ars Combinatoria}, Vol.~101, pp. 161--185, 2011.

\bibitem{char11}
I. CHARON, O. HUDRY and A. LOBSTEIN: Minimum sizes of identifying codes in graphs differing by one edge or one vertex, {\it Rapport interne Telecom ParisTech-2011D008}, Paris, France, 30 pages, 2011.

\bibitem{char09}
I. CHARON, O. HUDRY and A. LOBSTEIN: Extremal values for the maximum degree in a twin-free graph, {\it Ars Combinatoria}, Vol.~107, pp. 257--274, 2012.

\bibitem{char22}
I. CHARON, O. HUDRY and A. C. LOBSTEIN: Codes in the $q$-ary Lee hypercube, {\it WSEAS Transactions on Mathematics}, Vol.~21, pp. 173--186, 2022.

\bibitem{char00k}
G. CHARTRAND, L. EROH, M. A. JOHNSON and O. R. OELLERMANN: Resolvability in graphs and the metric dimension of a graph, {\it Discrete Applied Mathematics}, Vol. 105, pp. 99--113, 2000.

\bibitem{char02c}
G. CHARTRAND, D. ERWIN, M. A. HENNING, P. J. SLATER and P. ZHANG: The locating-chromatic number of a graph, {\it Bulletin of the Institute of Combinatorics and its Applications}, Vol.~36, pp. 89--101, 2002.

\bibitem{char03d}
G. CHARTRAND, D. ERWIN, M. A. HENNING, P. J. SLATER and P. ZHANG: Graphs of order $n$ with locating-chromatic number $n-1$, {\it Discrete Mathematics}, Vol.~269, pp. 65--79, 2003.

\bibitem{char03e}
G. CHARTRAND, D. ERWIN, P. J. SLATER and P. ZHANG: Distance-location numbers of graphs, {\it Utilitas Mathematica}, Vol.~63, pp. 65--79, 2003.

\bibitem{chel08}
M. CHELLALI: On locating and differentiating-total domination in trees, {\it Discussiones Mathematicae Graph Theory}, Vol.~28, pp. 383--392, 2008.

\bibitem{chel10}
M. CHELLALI, M. MIMOUNI and P. J. SLATER: On locating-domination in graphs, {\it Discussiones Mathematicae Graph Theory}, Vol.~30, pp. 223--235, 2010.

\bibitem{chel09}
M. CHELLALI and N. J. RAD: Locating-total domination critical graphs, {\it Australasian Journal of Combinatorics}, Vol.~45, pp. 227--234, 2009.

\bibitem{chel14}
M. CHELLALI, N. J. RAD, S. J. SEO and P. J. SLATER: On open neighborhood locating-dominating in graphs, {\it Electronic Journal of Graph Theory and Applications}, Vol.~2(2), pp. 87--98, 2014.

\bibitem{chen11}
C. CHEN, C. LU and Z. MIAO: Identifying codes and locating-dominating sets on paths and cycles, {\it Discrete Applied Mathematics}, Vol.~159, pp. 1540--1547, 2011.

\bibitem{chen11b}
X. CHEN and M. Y. SOHN: Bounds on the locating-total domination number of a tree, {\it Discrete Applied Mathematics}, Vol.~159, pp. 769--773, 2011.

\bibitem{cohe99a}
G. COHEN, S. GRAVIER, I. HONKALA, A. LOBSTEIN, M. MOLLARD, Ch. PAYAN and G. Z\'EMOR: Improved identifying codes for the grid, {\it Electronic Journal of Combinatorics}, Vol.~6(1), Comments to R19, 1999.\\
http://www.combinatorics.org

\bibitem{cohe99b}
G. COHEN, I. HONKALA, A. LOBSTEIN and G. Z\'EMOR: New bounds for codes identifying vertices in graphs, {\it Electronic Journal of Combinatorics}, Vol.~6(1), R19, 1999.\\
http://www.combinatorics.org

\bibitem{cohe00a}
G. COHEN, I. HONKALA, A. LOBSTEIN and G. Z\'EMOR: Bounds for codes identifying vertices in the hexagonal grid, {\it SIAM Journal on Discrete Mathematics}, Vol.~13, pp. 492--504, 2000.

\bibitem{cohe01a}
G. COHEN, I. HONKALA, A. LOBSTEIN and G. Z\'EMOR: On identifying codes, {\it Proceedings of DIMACS Workshop on Codes and Association Schemes '99}, Piscataway, USA, Vol.~56, pp. 97--109, 2001.

\bibitem{cohe01b}
G. COHEN, I. HONKALA, A. LOBSTEIN and G. Z\'EMOR: On codes identifying vertices in the two-dimensional square lattice with diagonals, {\it IEEE Transactions on Computers}, Vol.~50, pp. 174--176, 2001.

\bibitem{cohe99c}
G. COHEN, A. LOBSTEIN and G. Z\'EMOR: Identification d'une station d\'efaillante dans un contexte radio-mobile, Aspects Algorithmiques des T\'el\'ecommunications (AlgoTel '99), {\it Actes}, Roscoff, France, pp. 19--22, 1999.

\bibitem{cohe18}
N. COHEN and F. HAVET: On the minimum size of an identifying code over all orientations of a graph, {\it Electronic Journal of Combinatorics}, Vol. 25(1), P1.49, 2018.\\
http://www.combinatorics.org

\bibitem{cohe18k}
N. COHEN, N. A. MARTINS, F. MC~INERNEY, N. NISSE, S. P\'E\-RENNES and R. SAMPAIO: Spy-game on graphs: complexity and simple topologies, {\it Theoretical Computer Science}, Vol. 725, pp. 1--15, 2018.

\bibitem{colb87a}
C. J. COLBOURN, P. J. SLATER and L. K. STEWART: Locating dominating sets in series parallel networks, {\it Congressus Numerantium}, Vol.~56, pp. 135--162, 1987.

\bibitem{coup17}
P. COUPECHOUX: Extension of universal cycles for globally identifying colorings of cycles, {\it Discrete Mathematics}, Vol.~340, pp. 1456--1466, 2017.

\bibitem{cran09}
D. W. CRANSTON and G. YU: A new lower bound on the density of vertex identifying codes for the infinite hexagonal grid, {\it Electronic Journal of Combinatorics}, Vol.~16(1), R113, 2009.\\
http://www.combinatorics.org

\bibitem{cuki13}
A. CUKIERMAN and G. YU: New bounds on the minimum density of an identifying code for the infinite hexagonal grid, {\it Discrete Applied Mathematics}, Vol. 161, pp. 2910--2924, 2013.

\bibitem{dali14}
W. DALI and M. BLIDIA: Criticality indices of locating-domination of paths and cycles, {\it Utilitas Mathematica}, Vol.~94, pp. 199--219, 2014.

\bibitem{dali14b}
W. DALI and M. BLIDIA: On locating and locating-total domination edge addition critical graphs, {\it Utilitas Mathematica}, Vol.~94, pp. 303--313, 2014.

\bibitem{dani03}
M. DANIEL: Codes identifiants, {\it M\'emoire pour le DEA ROCO, Universit\'e Joseph Fourier}, Grenoble, France, June 2003.

\bibitem{dani04}
M. DANIEL, S. GRAVIER and J. MONCEL: Identifying codes in some subgraphs of the square lattice, {\it Theoretical Computer Science}, Vol.~319, pp. 411--421, 2004.

\bibitem{dant17}
R. DANTAS, F. HAVET and R. M. SAMPAIO: Identifying codes for infinite triangular grids with a finite number of rows, {\it Discrete Mathematics}, Vol.~340, pp. 1584--1597, 2017.

\bibitem{dant18b}
R. DANTAS, F. HAVET and R. M. SAMPAIO: Minimum density of identifying codes of king grids, {\it Discrete Mathematics}, Vol.~341, pp. 2708--2719, 2018.

\bibitem{dant18}
R. DANTAS, R. M. SAMPAIO and F. HAVET: Minimum density of identifying codes of king grids, {\it Electronic Notes in Discrete Mathematics}, Vol. 62, pp. 51--56, 2017.

\bibitem{debo03}
K. M. J. DE~BONTRIDDER, B. V. HALLD\'ORSSON, M. M. HALL\-D\'ORS\-SON, C. A. J. HURKENS, J. K. LENSTRA, R. RAVI and L. STOU\-GIE: Approximation algorithms for the test cover problem, {\it Mathematical Programming}, Vol.~98, pp. 477--491, 2003.

\bibitem{delm11}
O. DELMAS, S. GRAVIER, M. MONTASSIER and A. PARREAU: On two variations of identifying codes, {\it Discrete Mathematics}, Vol.~311, pp. 1948--1956, 2011.

\bibitem{dema22}
M. DEMANGE, A. DI~FONSO, G. DI~STEFANO and P. VITTORINI: A graph theoretical approach to the firebreak locating problem, {\it Theoretical Computer Science}, Vol. 914, pp. 47--72, 2022.

\bibitem{dey20}
S. DEY, F. FOUCAUD, S. C. NANDY and A. SEN: Discriminating codes in geometric setups, {\it Proceedings of 31st International Symposium on Algorithms and Computation (ISAAC 2020)}, Leibniz International Proceedings in Informatics, Vol. 181, 24:1--24:16, 2020.

\bibitem{dhal19a}
R. DHANALAKSHMI and C. DURAIRAJAN: Constructions of $r$-identifying codes and ($r,\leq \ell$)-identifying codes, {\it Indian Journal of Pure and Applied Mathematics}, Vol. 50, pp. 531--547, 2019.

\bibitem{dhal19b}
R. DHANALAKSHMI and C. DURAIRAJAN: $r$-identifying codes in binary Hamming space, $q$-ary Lee space and incomplete hypercube, {\it Discrete Mathematics, Algorithms and Applications}, Vol. 11(2), 1950027, 14 pages, 2019.

\bibitem{dhanC22}
R. DHANALAKSHMI and C. DURAIRAJAN: Bounds on $r$-identifying codes in $q$-ary Lee space, {\it Contributions to Discrete Mathematics}, Vol. 16(1), pp. 53--71, 2021.

\bibitem{entr74}
R. C. ENTRINGER and L. D. GASSMAN: Line-critical point determining and point distinguishing graphs, {\it Discrete Mathematics}, Vol.~10, pp. 43--55, 1974.

\bibitem{espe12}
L. ESPERET, S. GRAVIER, M. MONTASSIER, P. OCHEM and A. PARREAU: Locally identifying coloring of graphs, {\it Electronic Journal of Combinatorics}, Vol.~19(2), P40, 2012.\\
http://www.combinatorics.org

\bibitem{exoo99a}
G. EXOO: Computational results on identifying $t$-codes, {\it Preprint}, 1999.

\bibitem{exoo10}
G. EXOO, V. JUNNILA and T. LAIHONEN: On location-domination of set of vertices in cycles and paths, {\it Congressus Numerantium}, Vol.~202, pp. 97--112, 2010.

\bibitem{exoo09}
G. EXOO, V. JUNNILA and T. LAIHONEN: Locating-dominating codes in paths, {\it Discrete Mathematics}, Vol.~311, pp. 1863--1873, 2011.

\bibitem{exoo11}
G. EXOO, V. JUNNILA and T. LAIHONEN: Locating-dominating codes in cycles, {\it Australasian Journal of Combinatorics}, Vol.~49, pp. 177--194, 2011.

\bibitem{exoo08d}
G. EXOO, V. JUNNILA, T. LAIHONEN and S. RANTO: Locating vertices using codes, {\it Congressus Numerantium}, Vol. 191, pp. 143--159, 2008.

\bibitem{exoo08c}
G. EXOO, V. JUNNILA, T. LAIHONEN and S. RANTO: Upper bounds for binary identifying codes, {\it Advances in Applied Mathematics}, Vol. 42, pp. 277--289, 2009.

\bibitem{exoo08b}
G. EXOO, V. JUNNILA, T. LAIHONEN and S. RANTO: Improved bounds on identifying codes in binary Hamming spaces, {\it European Journal of Combinatorics}, Vol. 31, pp. 813--827, 2010.

\bibitem{exoo06}
G. EXOO, T. LAIHONEN and S. RANTO: Improved upper bounds on binary identifying codes, {\it IEEE Transactions on Information Theory}, Vol. IT-53, pp. 4255--4260, 2007.

\bibitem{exoo08}
G. EXOO, T. LAIHONEN and S. RANTO: New bounds on binary identifying codes, {\it Discrete Applied Mathematics}, Vol. 156, pp. 2250--2263, 2008.

\bibitem{fahl06}
T. FAHLE and K. TIEMANN: A faster branch-and-bound algorithm for the test-cover problem based on set-covering techniques, {\it ACM Journal of Experimental Algorithmics}, Vol.~11, 2006.

\bibitem{fazi16}
M. FAZIL, I. JAVAID, M. SALMAN and U. ALI: Locating-dominating sets in hypergraphs, {\it Periodica Mathematica Hungarica}, Vol. 72,  pp. 224--234, 2016.

\bibitem{fazl11}
N. FAZLOLLAHI, D. STAROBINSKI and A. TRACHTENBERG: Connecting identifying codes and fundamental bounds, {\it Proceedings of Information Theory and Applications Workshop, ITA 2011}, La Jolla, USA, pp. 403--409, 2011.

\bibitem{fazl11a}
N. FAZLOLLAHI, D. STAROBINSKI and A. TRACHTENBERG: Connected identifying codes for sensor network monitoring, {\it Proceedings of IEEE Wireless Communications and Networking Conference, WCNC 2011}, Cancun, Mexico, pp. 1026--1031, March 2011.

\bibitem{fazl12}
N. FAZLOLLAHI, D. STAROBINSKI and A. TRACHTENBERG: Connected identifying codes, {\it IEEE Transactions on Information Theory}, Vol. IT-58, pp. 4814--4824, 2012.

\bibitem{feng22}
M. FENG, X. MA and L. FENG: Optimal identifying codes of two families of Cayley graphs, {\it Discrete Applied Mathematics}, Vol.~320, pp. 199--210, 2022.

\bibitem{feng14}
M. FENG and K. WANG: Identifying codes of corona product graphs, {\it Discrete Applied Mathematics}, Vol.~169, pp. 88--96, 2014.

\bibitem{feng12}
M. FENG, M. XU and K. WANG: Identifying codes of lexicographic product of graphs, {\it Electronic Journal of Combinatorics}, Vol.~19(4), P56, 2012.\\
http://www.combinatorics.org

\bibitem{finb88a}
A. S. FINBOW and B. L. HARTNELL: On locating dominating sets and well-covered graphs, {\it Congressus Numerantium}, Vol.~65, pp. 191--200, 1988.

\bibitem{finb00a}
A. S. FINBOW and B. L. HARTNELL: Well-located graphs: a collection of well-covered ones, {\it Electronic Notes in Discrete Mathematics}, Vol.~5, 2000.

\bibitem{finb04a}
A. S. FINBOW and B. L. HARTNELL: Well-located graphs: a collection of well-covered ones, {\it Discrete Mathematics}, Vol.~276, pp. 201--209, 2004.

\bibitem{finb21}
A. S. FINBOW, B. L. HARTNELL and J. R. YOUNG: The complexity of monitoring a network with both watchers and listeners, {\it Journal of Combinatorial Mathematics and Combinatorial Computing}, Vol. 116, pp. 233--244, 2021.

\bibitem{fouc09}
F. FOUCAUD: Identifying codes in special graph classes, {\it M\'emoire de Master, Universit\'e de Bordeaux~1}, France, June 2009.\\
http://www.labri.fr/perso/foucaud/Research/MasterThesis

\bibitem{fouc12b}
F. FOUCAUD: Aspects combinatoires et algorithmiques des codes identifiants dans les graphes, {\it Th\`ese de Doctorat}, Universit\'e de Bordeaux~1, France, 194 pages, December 2012 (in English).

\bibitem{fouc13a}
F. FOUCAUD: The complexity of the  identifying code problem in restricted graph classes, {\it Lecture Notes in Computer Science}, No. 8288, pp. 150--163, Springer-Verlag, 2013.

\bibitem{fouc15}
F. FOUCAUD: Decision and approximation complexity for identifying codes and locating-dominating sets in restricted graph classes, {\it Journal of Discrete Algorithms}, Vol.~31, pp. 48--68, 2015.

\bibitem{fouc21q}
F. FOUCAUD, N. GHAREGHANI, A. ROSHANY-TABRIZI and P. SHARIANI: Characterizing extremal graphs for open neighbourhood location-domination, {\it Discrete Applied Mathematics}, Vol. 302, pp. 76--79, 2021.

\bibitem{fouc12a}
F. FOUCAUD, S. GRAVIER, R. NASERASR, A. PARREAU and P. VALICOV: Edge identifying codes, {\it Electronic Notes in Discrete Mathematics}, Vol.~38, pp. 343--348, 2011.

\bibitem{fouc11d}
F. FOUCAUD, S. GRAVIER, R. NASERASR, A. PARREAU and P. VALICOV: Identifying codes in line graphs, {\it Journal of Graph Theory}, Vol. 73, pp. 425--448, 2013.

\bibitem{fouc10a}
F. FOUCAUD, E. GUERRINI, M. KOV$\check{\textrm{S}}$E, R. NASERASR, A. PARREAU and P. VALICOV: On identifying codes and Bondy's theorem on ``induced subsets'', {\it Abstracts of the 8th French Combinatorial Conference}, Orsay, France, No.~125, 2010.

\bibitem{fouc10b}
F. FOUCAUD, E. GUERRINI, M. KOV$\check{\textrm{S}}$E, R. NASERASR, A. PARREAU and P. VALICOV: Classifying graphs with minimum identifying code of size $n-1$, {\it Abstracts of the 8th French Combinatorial Conference}, Orsay, France, No.~151, 2010.

\bibitem{fouc11a}
F. FOUCAUD, E. GUERRINI, M. KOV$\check{\textrm{S}}$E, R. NASERASR, A. PARREAU and P. VALICOV: Extremal graphs for the identifying code problem, {\it European Journal of Combinatorics}, Vol.~32, pp. 628--638, 2011.

\bibitem{fouc16}
F. FOUCAUD and M. A. HENNING: Location-domination and matching in cubic graphs, {\it Discrete Mathematics}, Vol.~339, pp. 1221--1231, 2016.

\bibitem{fouc16z}
F. FOUCAUD and M. A. HENNING: Locating-total dominating sets in twin-free graphs: a conjecture, {\it Electronic Journal of Combinatorics}, Vol. 23(3), P3.9, 2016.\\
http://www.combinatorics.org

\bibitem{fouc17}
F. FOUCAUD and M. A. HENNING: Location-domination in line graphs, {\it Discrete Mathematics}, Vol.~340, pp. 3140--3153, 2017.

\bibitem{fouc16a}
 F. FOUCAUD, M. A. HENNING, C. L\"{O}WENSTEIN and T. SASSE: Locating-dominating sets in twin-free graphs, {\it Discrete Applied Mathematics}, Vol.~200, pp. 52--58, 2016.

\bibitem{fouc20q}
F. FOUCAUD, S. HEYDARSHAHI and A. PARREAU: Domination and location in twin-free digraphs, {\it Discrete Applied Mathematics}, Vol.~284, pp. 42--52, 2020.

\bibitem{fouc12}
F. FOUCAUD, I. HONKALA, T. LAIHONEN, A. PARREAU and G. PERARNAU: Locally identifying colourings for graphs with given maximum degree, {\it Discrete Mathematics}, Vol.~312, pp. 1832--1837, 2012.

\bibitem{fouc17q}
F. FOUCAUD and R. KLASING: Parameterized and approximation complexity of the detection pair problem in graphs, {\it Journal of Graph Algorithms and Applications}, Vol. 21(6), pp. 1039--1056, 2017.

\bibitem{fouc11b}
F. FOUCAUD, R. KLASING, A. KOSOWSKI and A. RASPAUD: On the size of identifying codes in triangle-free graphs, {\it Discrete Applied Mathematics}, Vol.~160, pp. 1532--1546, 2012.

\bibitem{fouc10c}
F. FOUCAUD and M. KOV$\check{\textrm{S}}$E: On the identification of vertices in graphs using paths, {\it Abstracts of the 8th French Combinatorial Conference}, Orsay, France, No.~175, 2010.

\bibitem{fouc14}
F. FOUCAUD and M. KOV$\check{\textrm{S}}$E: On graph identification problems and the special case of identifying vertices using paths, {\it Lecture Notes in Computer Science}, No. 7643, pp. 32--45, 2012.

\bibitem{fouc13c}
F. FOUCAUD and M. KOV$\check{\textrm{S}}$E: Identifying path covers in graphs, {\it Journal of Discrete Algorithms}, Vol.~23, pp. 21--34, 2013.

\bibitem{fouc13}
F. FOUCAUD, T. LAIHONEN and A. PARREAU: An improved lower bound for $(1, \leq 2)$-identifying codes in the king grid, {\it Advances in Mathematics of Communications}, Vol.~8, pp. 35--52, 2014.

\bibitem{fouc22FL}
F. FOUCAUD and T. LEHTIL\"A: Revisiting and improving upper bounds for identifying codes, {\it SIAM Journal on Discrete Mathematics}, Vol. 36, pp. 2619--2634, 2022.

\bibitem{fouc16b}
F. FOUCAUD, G. B. MERTZIOS, R. NASERASR, A. PARREAU and P. VALICOV: Algorithms and complexity for metric dimension and location-domination on interval and permutation graphs, {\it Lecture Notes in Computer Science}, No. 9224, pp. 456--471, Springer-Verlag, 2016.

\bibitem{fouc17z}
F. FOUCAUD, G. B. MERTZIOS, R. NASERASR, A. PARREAU and P. VALICOV: Identification, location-domination and metric dimension on interval and permutation graphs: I. Bounds, {\it Theoretical Computer Science}, Vol.~668, pp. 43--58, 2017.

\bibitem{fouc17y}
F. FOUCAUD, G. B. MERTZIOS, R. NASERASR, A. PARREAU and P. VALICOV: Identification, location-domination and metric dimension on interval and permutation graphs: II. Algorithms and complexity, {\it Algorithmica}, Vol.~78, pp. 914--944, 2017.

\bibitem{fouc11}
F. FOUCAUD, R. NASERASR, and A. PARREAU: Characterizing extremal digraphs for identifying codes and extremal cases of Bondy's theorem on induced subsets, {\it Graphs and Combinatorics}, Vol.~29, pp. 463--473, 2013.

\bibitem{fouc11c}
F. FOUCAUD and G. PERARNAU: Bounds for identifying codes in terms of degree parameters, {\it Electronic Journal of Combinatorics}, Vol.~19(1), P32, 2012.\\
http://www.combinatorics.org

\bibitem{fouc17x}
F. FOUCAUD, G. PERARNAU and O. SERRA: Random subgraphs make identification affordable, {\it Journal of  Combinatorics}, Vol.~8, pp. 57--77, 2017.

\bibitem{fric07}
M. FRICK, G. H. FRICKE, C. M. MYNHARDT and R. D. SKAGGS: Critical graphs with respect to vertex identification, {\it Utilitas Mathematica}, Vol.~76, pp. 213--227, 2008.

\bibitem{frie06}
A. FRIEZE, R. MARTIN, J. MONCEL, M. RUSZINK\'O and C. SMYTH: Codes identifying sets of vertices in random networks, {\it Discrete Mathematics}, Vol.~307, pp. 1094--1107, 2007.

\bibitem{gari14}
D. GARIJO, A. GONZ\'ALEZ and A. M\'ARQUEZ: The difference between the metric dimension and the determining number of a graph, {\it Applied Mathematics and Computation}, Vol.~ 249, pp. 487--501, 2014.

\bibitem{garn93a}
D. K. GARNICK, Y. H. H. KWONG and F. LAZEBNIK: Extremal graphs without three-cycles or four-cycles, {\it Journal of Graph Theory}, Vol.~17, pp. 633--645, 1993.

\bibitem{garn95a}
D. K. GARNICK, Y. H. H. KWONG and F. LAZEBNIK: Algorithmic search for extremal graphs of girth at least five, {\it Graph Theory, Combinatorics, and Applications: Proceedings of the 7th Quadrennial International Conference on the Theory and Applications of Graphs}, Vol.~2, pp. 697--709, Wiley, 1995.

\bibitem{garn92a}
D. K. GARNICK and N. A. NIEUWEJAAR: Nonisomorphic extremal graphs without three-cycles or four-cycles, {\it Journal of Combinatorial Mathematics and Combinatorial Computing}, Vol.~12, pp. 33--56, 1992.

\bibitem{gheb13}
M. GHEBLEH and L. NIEPEL: Locating and identifying codes in circulant networks, {\it Discrete Applied Mathematics}, Vol.~161, pp. 2001--2007, 2013.

\bibitem{ghor20}
M. GHORBANI, M. DEHMER, H. MAIMANI, S. MADDAH, M. ROOZ\-BAYANI and F. EMMERT-STREIB: The watching system as a generalization of identifying code, {\it Applied Mathematics and Computation}, Vol. 380, 125302, 7 pages, 2020.

\bibitem{ghorm21}
M. GHORBANI and S. MADDAH: On the watching number of graphs using discharging procedure, {\it Journal of Applied Mathematics and Computing}, Vol. 67, pp. 507--518, 2021.

\bibitem{gimb01}
J. GIMBEL, B. D. VAN~GORDEN, M. NICOLESCU, C. UMSTEAD and N. VAIANA: Location with dominating sets, {\it Congressus Numerantium}, Vol.~151, pp. 129--144, 2001.

\bibitem{give18}
R. M. GIVENS: Mixed-weight open locating dominating sets, {\it Ph. D. Thesis}, The College of William and Mary, Virginia, USA, 2018.

\bibitem{give17}
R. M. GIVENS, R. K. KINCAID, W. MAO and G. YU: Mixed-weight open locating-dominating sets, {\it Proceedings of 51st Annual Conference on Information Sciences and Systems (CISS)}, pp. 1--6, 2017.

\bibitem{give20}
R. M. GIVENS, G. YU and R. K. KINCAID: Open-locating domination sets in circulant graphs, {\it Discussiones Mathematicae Graph Theory}, Vol.~42(1), pp. 47--62, 2022.

\bibitem{gled19}
V. GLEDEL and A. PARREAU: Identification of points using disks, {\it Discrete Mathematics}, Vol. 342, pp. 256--269, 2019.

\bibitem{godd13}
W. GODDARD and K. WASH: ID codes in Cartesian products of cliques, {\it Journal of Combinatorial Mathematics and Combinatorial Computing}, Vol.~85, pp. 97--106, 2013.

\bibitem{gonc13}
D. GON\c~CALVES, A. PARREAU and A. PINLOU: Locally identifying coloring in bounded expansion classes of graphs, {\it Discrete Applied Mathematics}, Vol.~161, pp. 2946--2951, 2013.

\bibitem{gonz18}
A. GONZ\'ALEZ, C. HERNANDO and  M. MORA: Metric-locating-dominating sets of graphs for constructing related subsets of vertices, {\it Applied Mathematics and Computation}, Vol. 332, pp. 449--456, 2018.

\bibitem{grap08}
R. GRAPPE, N. BRAUNER and J. MONCEL: Un probl\`eme de surveillance : mod\'elisation et simulation avec la th\'eorie des jeux, {\it Abstracts of 9\`eme Congr\`es de la Soci\'et\'e Fran\c{c}aise de Recherche Op\'erationnelle et d'Aide \`a la D\'ecision, ROADEF 08}, Clermont-Ferrand, France, pp. 221--222, February 2008.

\bibitem{grav14}
S. GRAVIER, S. JANSON, T. LAIHONEN and S. RANTO: Graphs where every $k$-subset of vertices is an identifying set, {\it Discrete Mathematics \& Theoretical Computer Science}, Vol.~16, pp. 73--88, 2014.

\bibitem{grav08}
S. GRAVIER, R. KLASING and J. MONCEL: Hardness results and approximation algorithms for identifying codes and locating-dominating codes in graphs, {\it Algorithmic Operations Research}, Vol.~3, pp. 43--50, 2008.

\bibitem{grav13}
S. GRAVIER, M. KOV$\check{\textrm{S}}$E, M. MOLLARD, J. MONCEL and A. PARREAU: New results on variants of covering codes in Sierpi\'nski graphs, {\it Designs, Codes and Cryptography}, Vol.~69, pp. 181--188, 2013.

\bibitem{grav05}
S. GRAVIER and J. MONCEL: Construction of codes identifying sets of vertices, {\it Electronic Journal of Combinatorics}, Vol.~12(1), R13, 2005.\\
http://www.combinatorics.org

\bibitem{grav04}
S. GRAVIER and J. MONCEL: On graphs having a $V \setminus \{ x \}$ set as an identifying code, {\it Discrete Mathematics}, Vol.~307, pp. 432--434, 2007.

\bibitem{grav04b}
S. GRAVIER, J. MONCEL and A. SEMRI: Identifying codes of cycles, {\it European Journal of Combinatorics}, Vol.~27, pp. 767--776, 2006.

\bibitem{grav08b}
S. GRAVIER, J. MONCEL and A. SEMRI: Identifying codes of Cartesian product of two cliques of the same size, {\it Electronic Journal of Combinatorics}, Vol.~15(1), N4, 2008.\\
http://www.combinatorics.org

\bibitem{grav16}
S. GRAVIER, A. PARREAU, S. ROTTAY, L. STORME and E. VANDOMME: Identifying codes in vertex-transitive graphs and strongly regular graphs, {\it Electronic Journal of Combinatorics}, Vol.~22(4), P4.6, 2015.\\
http://www.combinatorics.org

\bibitem{hafi22}
Y. HAFIDH and E. T. BASKORO: On the locating chromatic number of trees, {\it International Journal of Mathematics and Computer Science}, Vol. 17, pp. 377--394, 2022.

\bibitem{haka20k}
A. HAKANEN, V. JUNNILA and T. LAIHONEN: The solid-metric dimension, {\it Theoretical Computer Science}, Vol. 806, pp. 156--170, 2020.

\bibitem{haka22A}
A. HAKANEN, V. JUNNILA, T. LAIHONEN and I. G. YERO: On vertices contained in all or in no metric basis, {\it Discrete Applied Mathematics}, Vol. 319, pp. 407--423, 2022.

\bibitem{haka18}
A. HAKANEN and T. LAIHONEN: On $\{\ell\}$-metric dimensions in graphs, {\it Fundamenta Informaticae}, Vol.~162, pp. 143--160, 2018.

\bibitem{hall01}
B. V. HALLD\'ORSSON, M. M. HALLD\'ORSSON and R. RAVI: On the approximability of the minimum collection problem, {\it Lecture Notes in Computer Science}, No. 2161, pp. 158--169, Springer-Verlag, 2001.

\bibitem{hara76}
F. HARARY and R. A. MELTER: On the metric dimension of a graph, {\it Ars Combinatoria}, Vol.~2, pp. 191--195, 1976.

\bibitem{hara77}
F. HARARY and R. A. MELTER: Addendum to ``On the metric dimension of a graph'' (Ars Combinatoria 2 (1976) 191--195), {\it Ars Combinatoria}, Vol.~4, p. 318, 1977.

\bibitem{hata05}
H. HATAMI: $\Delta +300$ is a bound on the adjacent vertex distinguishing edge chromatic number, {\it Journal of Combinatorial Theory}, Ser. B, Vol.~95, pp. 246--256, 2005.

\bibitem{have10}
F. HAVET: Minimum-density identifying codes in grids, {\it Unpublished manuscript}, 2010.

\bibitem{have14}
F. HAVET, N. PARAMAGURU and R. SAMPATHKUMAR: Detection number of bipartite graphs and cubic graphs, {\it Discrete Mathematics and Theoretical Computer Science}, Vol. 16, pp. 333--342, 2014.

\bibitem{hayn98a}
T. W. HAYNES, S. T. HEDETNIEMI and P. J. SLATER: Fundamentals of Domination in Graphs, {\it CRC press}, New York, Marcel Dekker, 1998.

\bibitem{hayn06}
T. W. HAYNES, M. A. HENNING and J. HOWARD: Locating and total dominating sets in trees, {\it Discrete Applied Mathematics}, Vol.~154, pp. 1293--1300, 2006.

\bibitem{hayn09}
T. W. HAYNES, K. R. S. HOLMES, D. R. KOESSLER and L. SEWELL: Locating-domination in complementary prisms of paths and cycles, {\it Congressus Numerantium}, Vol.~199, pp. 45--55, 2009.

\bibitem{hede15}
J. HEDETNIEMI: On identifying codes in the Cartesian product of a path and a complete graph, {\it Journal of Combinatorial Optimization}, Vol.~31, pp. 1405--1416, 2016.

\bibitem{henn12c}
M. A. HENNING and C. L\"{O}WENSTEIN: Locating-total domination in claw-free cubic graphs, {\it Discrete Mathematics}, Vol.~312, pp. 3107--3116, 2012.

\bibitem{henn04}
M. A. HENNING and O. R. OELLERMANN: Metric-locating-dominating sets in graphs, {\it Ars Combinatoria}, Vol.~73, pp. 129--141, 2004.

\bibitem{henn12b}
M. A. HENNING and N. J. RAD: Locating-total domination in graphs, {\it Discrete Applied Mathematics}, Vol.~160, pp. 1986--1993, 2012.

\bibitem{henn12}
M. A. HENNING and A. YEO: Identifying vertex covers in graphs, {\it Electronic Journal of Combinatorics}, Vol.~19(4), P32, 2012.\\
http://www.combinatorics.org

\bibitem{henn13}
M. A. HENNING and A. YEO: Distinguishing-transversal in hypergraphs and identifying open codes in cubic graphs, {\it Graphs and Combinatorics}, Vol.~30, pp. 909--932, 2014.

\bibitem{hern14}
C. HERNANDO, M. MORA and I. M. PELAYO: Nordhaus-Gaddum bounds for locating domination, {\it European Journal of Combinatorics}, Vol. 36, pp. 1--6, 2014.

\bibitem{hern15}
C. HERNANDO, M. MORA and I. M. PELAYO: On global location-domination in graphs, {\it Ars Mathematica Contemporanea}, Vol. 8, pp. 365--379, 2015.

\bibitem{hern19}
C. HERNANDO, M. MORA and I. M. PELAYO: Locating domination in bipartite graphs and their complements, {\it Discrete Applied Mathematics}, Vol. 263, pp. 195--203, 2019.

\bibitem{hern10}
C. HERNANDO, M. MORA, I. M. PELAYO, C. SEARA and D. R. WOOD: Extremal graph theory for metric dimension and diameter, {\it Electronic Journal of Combinatorics}, Vol.~17(1), R30, 2010.\\
http://www.combinatorics.org

\bibitem{heyd18}
S. HEYDARSHAHI: Location-domination in twin-free graphs and digraphs, {\it Master's Thesis, Universit\'e Paris Sorbonne}, 2018.

\bibitem{hiss13}
A. HISSOUM and A. SEMRI: Identifying codes of Cartesian product of two cliques, {\it Proceedings of 2013 International Conf. on Applied Mathematics and Computational Methods}, pp. 104--108, 2013.

\bibitem{hocq14}
H. HOCQUARD and M. MONTASSIER: Adjacent vertex-distinguishing edge coloring of graphs with maximum degree~$\Delta$, {\it Journal of Combinatorial Optimization}, Vol. 26, pp. 152--160, 2013.

\bibitem{holm09}
K. R. S. HOLMES: Locating-domination in complementary prisms, {\it Master's Thesis, East Tennessee State University}, USA, 37 pages, 2009.

\bibitem{holm10}
K. R. S. HOLMES, D. R. KOESSLER and T. W. HAYNES: Locating-domination in complementary prisms, {\it Journal of Combinatorial Mathematics and Combinatorial Computing}, Vol.~72, pp. 163--171, 2010.

\bibitem{honk99a}
I. HONKALA: On the identifying radius of codes, {\it Proceedings of the 7th Nordic Combinatorial Conference}, Turku, Finland, pp. 39--43, 1999.

\bibitem{honk02e}
I. HONKALA: Triple systems identifying quadruples, {\it Australasian Journal of Combinatorics}, Vol.~25, pp. 303--316, 2002.

\bibitem{honk03d}
I. HONKALA: An optimal edge-robust identifying code in the triangular lattice, {\it Annals of Combinatorics}, Vol.~8, pp. 303--323, 2004.

\bibitem{honk06a}
I. HONKALA: A family of optimal identifying codes in $Z^2$, {\it Journal of Combinatorial Theory}, Ser. A, Vol.~113, pp. 1760--1763, 2006.

\bibitem{honk05a}
I. HONKALA: An optimal locating-dominating set in the infinite triangular grid, {\it Discrete Mathematics}, Vol.~306, pp. 2670--2681, 2006.

\bibitem{honk06b}
I. HONKALA: On 2-edge-robust $r$-identifying codes in the king grid, {\it Australasian Journal of Combinatorics}, Vol.~36, pp. 151--165, 2006.

\bibitem{honk08}
I. HONKALA: On $r$-locating-dominating sets in paths, {\it European Journal of Combinatorics}, Vol. 30, pp. 1022--1025, 2009.

\bibitem{honk10}
I. HONKALA: An optimal strongly identifying code in the infinite triangular grid, {\it Electronic Journal of Combinatorics}, Vol.~17(1), R91, 2010.\\
http://www.combinatorics.org

\bibitem{honk14c}
 I. HONKALA, O. HUDRY and A. LOBSTEIN: On the number of optimal identifying codes in a twin-free graph, {\it Discrete Applied Mathematics}, Vol.~180, pp. 111--119, 2015.

\bibitem{honk14a}
 I. HONKALA, O. HUDRY and A. LOBSTEIN: On the ensemble of optimal dominating and locating-dominating codes in a graph, {\it Information Processing Letters}, Vol.~115, pp. 699--702, 2015.

\bibitem{honk14b}
 I. HONKALA, O. HUDRY and A. LOBSTEIN: On the ensemble of optimal identifying codes in a twin-free graph, {\it Cryptography and Communications -- Discrete Structures, Boolean Functions and Sequences}, Vol.~8, pp. 139--153, 2016.

\bibitem{honk06f}
I. HONKALA, M. G. KARPOVSKY and L. B. LEVITIN: On robust and dynamic identifying codes, {\it IEEE Transactions on Information Theory}, Vol. IT-52, pp. 599--612, 2006.

\bibitem{honk01c}
I. HONKALA, M. G. KARPOVSKY and S. LITSYN: On the identification of vertices and edges using cycles, {\it Lecture Notes in Computer Science}, No. 2227, pp. 308--314, Springer-Verlag, 2001.

\bibitem{honk04b}
I. HONKALA, M. G. KARPOVSKY and S. LITSYN: Cycles identifying vertices and edges in binary hypercubes and 2-dimensional tori, {\it Discrete Applied Mathematics}, Vol.~129, pp. 409--419, 2003.

\bibitem{honk03b}
I. HONKALA and T. LAIHONEN: On the identification of sets of points in the square lattice, {\it Discrete \& Computational Geometry}, Vol.~29, pp. 139--152, 2003.

\bibitem{honk03c}
I. HONKALA and T. LAIHONEN: On identification of sets of vertices in the triangular grid, {\it Proceedings of Workshop on Coding and Cryptography 2003}, Versailles, France, pp. 265--271, 2003.

\bibitem{honk04e}
I. HONKALA and T. LAIHONEN: Codes for identification in the king lattice, {\it Graphs and Combinatorics}, Vol.~19, pp. 505--516, 2003.

\bibitem{honk04c}
I. HONKALA and T. LAIHONEN: On identifying codes in the hexagonal mesh, {\it Information Processing Letters}, Vol.~89, pp. 9--14, 2004.

\bibitem{honk04d}
I. HONKALA and T. LAIHONEN: On identifying codes in the triangular and square grids, {\it SIAM Journal on Computing}, Vol.~33, pp. 304--312, 2004.

\bibitem{honk04f}
I. HONKALA and T. LAIHONEN: On identification in the triangular grid, {\it Journal of Combinatorial Theory}, Ser. B, Vol.~91, pp. 67--86, 2004.

\bibitem{honk05c}
I. HONKALA and T. LAIHONEN: On locating-dominating sets in infinite grids, {\it European Journal of Combinatorics}, Vol.~27, pp. 218--227, 2006.

\bibitem{honk04g}
I. HONKALA and T. LAIHONEN: On a new class of identifying codes in graphs, {\it Information Processing Letters}, Vol.~102, pp. 92--98, 2007.

\bibitem{honk06d}
I. HONKALA and T. LAIHONEN: On identifying codes that are robust against edge changes, {\it Information and Computation}, Vol.~205, pp. 1078--1095, 2007.

\bibitem{honk06c}
I. HONKALA and T. LAIHONEN: On identifying codes in the king grid that are robust against edge deletions, {\it Electronic Journal of Combinatorics}, Vol.~15(1), R3, 2008.\\
http://www.combinatorics.org

\bibitem{honk06e}
I. HONKALA and T. LAIHONEN: On vertex-robust identifying codes of level three, {\it Ars Combinatoria}, Vol.~94, pp. 115--127, 2010.

\bibitem{honk01a}
I. HONKALA, T. LAIHONEN and S. RANTO: On codes identifying sets of vertices in Hamming spaces, {\it Designs, Codes and Cryptography}, Vol.~24, pp. 193--204, 2001.

\bibitem{honk01b}
I. HONKALA, T. LAIHONEN and S. RANTO: Codes for strong identification, {\it Proceedings of Workshop on Coding and Cryptography 2001}, Paris, France, pp. 279--287, 2001.

\bibitem{honk02d}
I. HONKALA, T. LAIHONEN and S. RANTO: On strongly identifying codes, {\it Discrete Mathematics}, Vol.~254, pp. 191--205, 2002.

\bibitem{honk04a}
I. HONKALA, T. LAIHONEN and S. RANTO: On locating-dominating codes in binary Hamming spaces, {\it Discrete Mathematics and Theoretical Computer Science}, Vol.~6, pp. 265--282, 2004.

\bibitem{honk02a}
I. HONKALA and A. LOBSTEIN: On the density of identifying codes in the square lattice, {\it Journal of Combinatorial Theory}, Ser. B, Vol.~85, pp. 297--306, 2002.

\bibitem{honk02b}
I. HONKALA and A. LOBSTEIN: On identifying codes in binary Hamming spaces, {\it Journal of Combinatorial Theory}, Ser. A, Vol.~99, pp. 232--243, 2002.

\bibitem{honk02c}
I. HONKALA and A. LOBSTEIN: On the complexity of the identification problem in Hamming spaces, {\it Acta Informatica}, Vol.~38, pp. 839--845, 2002.

\bibitem{honk02f}
I. HONKALA and A. LOBSTEIN: Identifying vertices in the $n$-cube, {\it Proceedings of the 8th International Workshop on Algebraic and Combinatorial Coding Theory}, Tsarskoe Selo, Russia, pp. 198--201, 2002.

\bibitem{honk03a}
I. HONKALA and A. LOBSTEIN: On identification in $Z^2$ using translates of given patterns, {\it Journal of Universal Computer Science}, Vol.~9(10), pp. 1204--1219, October 2003.\\
http://www.jucs.org

\bibitem{hora17}
V. HORAN, S. ADACHI and S. BAK: A comparison of approaches for finding minimum identifying codes on graphs, {\it Quantum Information Processing}, Vol.~15, pp. 1827--1848, 2016.

\bibitem{howa04}
J. M. HOWARD: Locating and total dominating sets in trees, {\it Master's Thesis, East Tennessee State University}, USA, 48 pages, 2004.

\bibitem{hudr15a}
O. HUDRY and A. LOBSTEIN: More results on the complexity of identifying problems in graphs, {\it Theoretical Computer Science}, Vol.~626, pp. 1--12, 2016.

\bibitem{hudr16}
O. HUDRY and A. LOBSTEIN: Some results about a conjecture on identifying codes in complete suns, {\it International Transactions in Operational Research}, Vol.~26, pp. 732--746, 2019.

\bibitem{hudr18a}
O. HUDRY and A. LOBSTEIN: Unique (optimal) solutions: Complexity results for identifying and locating-dominating codes, {\it Theoretical Computer Science}, Vol. 767, pp. 83--102, 2019.

\bibitem{hudr18z}
O. HUDRY and A. LOBSTEIN: The compared costs of domination, location-domination and identification, {\it Discussiones Mathematicae Graph Theory}, Vol.~40(1), pp. 127--147, 2020.\\
http://www.discuss.wmie.uz.zgora.pl/gt/index.php?doi=10.7151/dmgt.2129

\bibitem{hudr20z}
O. HUDRY and A. LOBSTEIN: Some rainbow problems in graphs have complexity equivalent to satisfiability problems, {\it International Transactions in Operational Research}, Vol.~29(3), pp. 1547--1572, 2022.

\bibitem{inay21}
N. INAYAH, W. ARIBOWO and M. M. WINDRA~YAHYA: The locating chromatic number of book graph, {\it Journal of Mathematics}, Paper ID 3716361, 3 pages, 2021.

\bibitem{iswa11}
H. ISWADI, E. T. BASKORO and R. SIMANJUNTAK: On the metric dimension of corona product of graphs, {\it Far East Journal of Mathematical Sciences}, Vol.~52(2), pp. 155--170, 2011.

\bibitem{jans08}
S. JANSON and T. LAIHONEN: An optimal result for codes identifying sets of words, {\it Proceedings of the 2009 IEEE International Symposium on Information Theory}, pp. 2547--2551, 2009.

\bibitem{jans09}
S. JANSON and T. LAIHONEN: On the size of identifying codes in binary hypercubes, {\it Journal of Combinatorial Theory}, Ser. A, Vol.~116, pp. 1087--1096, 2009.

\bibitem{jayag16}
R. JAYAGOPAL, I. RAJASINGH and R. S. RAJAN: Domination parameters in hypertrees, {\it Lecture Notes in Computer Science}, No. 9602, pp. 299--307, Springer-Verlag, 2016.

\bibitem{jean22}
D. C. JEAN and S. J. SEO: Extremal cubic graphs for fault-tolerant locating domination, {\it Theoretical Computer Science}, Vol.~917, pp. 94--106, 2022.

\bibitem{jean23}
D. C. JEAN and S. J. SEO: Optimal error-detecting open-locating-dominating set on the infinite triangular grid, {\it Discussiones Mathematicae Graph Theory}, Vol.~43(2), pp. 445--455, 2023.

\bibitem{jeanAP1}
D. C. JEAN and S. J. SEO: Fault-tolerant identifying codes in special classes of graphs, {\it Discussiones Mathematicae Graph Theory}, to appear.

\bibitem{jeanAP2}
D. C. JEAN and S. J. SEO: Progress on fault-tolerant locating-dominating sets, {\it Discrete Mathematics, Algorithms and Applications}, to appear.

\bibitem{jian18}
M. JIANG: Periodicity of identifying codes in strips, {\it Information Processing Letters}, Vol. 135, pp. 77--84, 2018.

\bibitem{junn11a}
V. JUNNILA: On identifying and locating-dominating codes, {\it Ph. D. Thesis}, University of Turku, Finland, 125 pages, 2011.

\bibitem{junn12}
V. JUNNILA: Adaptive identification of sets of vertices in graphs, {\it Discrete Mathematics and Theoretical Computer Science}, Vol.~14, pp. 69--86, 2012.

\bibitem{junn13}
V. JUNNILA: New lower bound for 2-identifying code in the square grid, {\it Discrete Applied Mathematics}, Vol.~161, pp. 2042--2051, 2013.

\bibitem{junn15}
V. JUNNILA: Optimal locating-total dominating sets in strips of height~3, {\it Discussiones Mathematicae Graph Theory}, Vol.~35, pp. 447--462, 2015.

\bibitem{junn11}
V. JUNNILA and T. LAIHONEN: Identification in~$Z^2$ using Euclidean balls, {\it Discrete Applied Mathematics}, Vol.~159, pp. 335--343, 2011.

\bibitem{junn09a}
V. JUNNILA and T. LAIHONEN: Optimal identifying codes in cycles and paths, {\it Graphs and Combinatorics}, Vol.~28, pp. 469--481, 2012.

\bibitem{junn12b}
V. JUNNILA and T. LAIHONEN: Optimal lower bound for 2-identifying codes in the hexagonal grid, {\it Electronic Journal of Combinatorics}, Vol.~19(2), P38, 2012.\\
http://www.combinatorics.org

\bibitem{junn14}
V. JUNNILA and T. LAIHONEN: Optimal identification of sets of edges using $2$-factors, {\it Discrete Mathematics}, Vol.~313, pp. 1636--1647, 2013.

\bibitem{junn15a}
V. JUNNILA and T. LAIHONEN: Codes for information retrieval with small uncertainty, {\it IEEE Transactions on Information Theory}, Vol. IT-60, pp. 976--985, 2014.

\bibitem{junn15b}
  V. JUNNILA and T. LAIHONEN: Information retrieval with unambiguous output, {\it Information and Computation}, Vol.~242, pp. 354--368, 2015.

\bibitem{junn16}
V. JUNNILA and T. LAIHONEN: Information retrieval with varying number of input clues, {\it IEEE Transactions on Information Theory}, Vol. IT-62, pp. 625--638, 2016.

\bibitem{junn16a}
V. JUNNILA and T. LAIHONEN: Minimum number of input clues in robust information retrieval, {\it Fundamenta Informaticae}, Vol. 145(3), pp. 243--256, 2016.

\bibitem{junn16c}
V. JUNNILA and T. LAIHONEN: Collection of codes for tolerant location, {\it Proceedings of the Bordeaux Graph Workshop}, Bordeaux, France, pp. 176--179, 2016.

\bibitem{junn20o}
V. JUNNILA and T. LAIHONEN: Tolerant location detection in sensor networks, {\it Advances in Applied Mathematics}, Vol. 112, 101938, 2020.

\bibitem{junn18}
V. JUNNILA, T. LAIHONEN and T. LEHTIL\"A: On regular and new types of codes for location-domination, {\it Discrete Applied Mathematics}, Vol.~247, pp. 225--241, 2018.

\bibitem{junn19j}
V. JUNNILA, T. LAIHONEN and T. LEHTIL\"A: On a conjecture regarding identification in Hamming graphs, {\it Electronic Journal of Combinatorics}, Vol. 26(2), P45, 2019.\\
http://www.combinatorics.org

\bibitem{junn20i}
V. JUNNILA, T. LAIHONEN and T. LEHTIL\"A: New results on codes for location in graphs, {\it Proceedings of Russian Finnish Symposium on Discrete Mathematics}, pp. 105--116, 2019.

\bibitem{junn21q}
V. JUNNILA, T. LAIHONEN and T. LEHTIL\"A: On Levenshtein's channel and list size in information retrieval, {\it IEEE Transactions on Information Theory}, Vol. 67(6), pp. 3322--3341, 2021.

\bibitem{junn22JLL}
V. JUNNILA, T. LAIHONEN and T. LEHTIL\"A: Improved lower bound for locating-dominating codes in binary Hamming spaces, {\it Designs, Codes and Cryptography}, vol. 90, pp. 67--85, 2022.

\bibitem{junn19e}
V. JUNNILA, T. LAIHONEN, T. LEHTIL\"A and M. L. PUERTAS: On stronger types of locating-dominating codes, {\it Discrete Mathematics and Theoretical Computer Science}, Vol. 21(1), Paper No.~1, 21 pages, 2019.

\bibitem{junn19c}
V. JUNNILA, T. LAIHONEN and G. PARIS: Location in circulant graphs, {\it Proceedings of the Fourth Russian-Finnish Symposium on Discrete Mathematics}, Turku, Finland, pp. 81--84, 2017.

\bibitem{junn19}
V. JUNNILA, T. LAIHONEN and G. PARIS: Optimal bounds on codes for location in circulant graphs, {\it Cryptography and Communications}, Vol.~11(4), pp. 621--640, 2019.

\bibitem{junn19a}
V. JUNNILA, T. LAIHONEN and G. PARIS: Solving two conjectures regarding codes for location in circulant graphs, {\it Discrete Mathematics and Theoretical Computer Science}, Vol. 21(3), Paper No.~2, 20 pages, 2019.

\bibitem{junn11b}
V. JUNNILA, T. LAIHONEN and A. PARREAU: Tolerant identification with Euclidean balls, {\it Networks}, Vol.~61, pp. 212--225, 2013.

\bibitem{kang22}
C. X. KANG and E. YI: Distance-$k$ locating-dominating sets in graphs, {\it Bulletin of the Institute of Combinatorics and its Applications}, Vol. 95, pp. 38--56, 2022.

\bibitem{karp98a}
M. G. KARPOVSKY, K. CHAKRABARTY and L. B. LEVITIN: On a new class of codes for identifying vertices in graphs, {\it IEEE Transactions on Information Theory}, Vol. IT-44, pp. 599--611, 1998.

\bibitem{karp99a}
M. G. KARPOVSKY, K. CHAKRABARTY, L. B. LEVITIN and D. R. AVRESKY: On the covering of vertices for fault diagnosis in hypercubes, {\it Information Processing Letters}, Vol.~69, pp. 99--103, 1999.

\bibitem{kim05}
J. H. KIM, O. PIKHURKO, J. H. SPENCER and O. VERBITSKY: How complex are random graphs in first order logic?, {\it Random Structures \& Algorithms}, Vol.~126, pp. 119--145, 2005.

\bibitem{kim10}
J. L. KIM and S. J. KIM: Identifying codes in $q$-ary hypercubes, {\it Bulletin of the Institute of Combinatorics and its Applications}, Vol.~59, pp. 93--102, 2010.

\bibitem{kim15}
Y. KIM, M. KUMBHAT, Z. L. NAGY, B. PATK\'OS, A. POKROVSKIY and M. VIZER: Identifying codes and searching with balls in graphs, {\it Discrete Applied Mathematics}, Vol.~193, pp. 39--47, 2015.

\bibitem{kina18}
M. KINAWI, Z. HUSSAIN and L. NIEPEL: Minimal locating-paired-dominating sets in triangular and king grids, {\it Kuwait Journal of Science}, Vol. 45(3), pp. 39--45, 2018.

\bibitem{kinc19}
R. K. KINCAID and R. M. GIVENS: Tabu search for a mixed strength sensor location problem, {\it Proceedings of the 2019 MODSIM World Conference}, Norfolk, USA, 2019.

\bibitem{kinc15}
R. KINCAID, A. OLDHAM and G. YU: Optimal open-locating-dominating sets in infinite triangular grids, {\it Discrete Applied Mathematics}, Vol.~193, pp. 139--144, 2015.

\bibitem{lai15}
P. L. LAI: Paths and cycles identifying vertices in twisted cubes, {\it Applied Mathematics and Computation}, Vol.~259, pp. 620--627, 2015.

\bibitem{laif07b}
M. LAIFENFELD: Coding for network applications: robust identification and distributed resource allocation, {\it Ph. D. Thesis}, University of Boston, USA, 2007.

\bibitem{laif11}
M. LAIFENFELD: Localization and identification in networks using robust identifying codes, {\it Proceedings of Information Theory and Applications Workshop, ITA 2008}, pp. 165--174, 2008.

\bibitem{laif05}
M. LAIFENFELD and A. TRACHTENBERG: Disjoint identifying-codes for arbitrary graphs, {\it Proceedings of the 2005 IEEE International Symposium on Information Theory}, Adelaide, Australia, pp. 244--248, September 2005.

\bibitem{laif08}
M. LAIFENFELD and A. TRACHTENBERG: Identifying codes and covering problems, {\it IEEE Transactions on Information Theory}, Vol. IT-54, pp. 3929--3950, 2008.

\bibitem{laif06}
M. LAIFENFELD, A. TRACHTENBERG and T. Y. BERGER-WOLF: Identifying codes and the set cover problem, {\it Proceedings of the 44th Annual Allerton Conf. on Communication, Control and Computing}, Monticello, USA, September 2006.

\bibitem{laif07}
M. LAIFENFELD, A. TRACHTENBERG, R. COHEN and D. STARO\-BINSKI: Joint monitoring and routing in wireless sensor networks using robust identifying codes, {\it Proceedings of IEEE Broadnets 2007}, Raleigh, USA, pp. 197--206, September 2007.

\bibitem{laih02a}
T. LAIHONEN: Sequences of optimal identifying codes, {\it IEEE Transactions on Information Theory}, Vol. IT-48, pp. 774--776, 2002.

\bibitem{laih02c}
T. LAIHONEN: Optimal codes for strong identification, {\it European Journal of Combinatorics}, Vol.~23, pp. 307--313, 2002.

\bibitem{laih05b}
T. LAIHONEN: On optimal edge-robust and vertex-robust $(1,\leq\ell)$-identifying codes, {\it SIAM Journal on Discrete Mathematics}, Vol.~18, pp. 825--834, 2005.

\bibitem{laih06b}
T. LAIHONEN: On robust identification in the square and king grids, {\it Discrete Applied Mathematics}, Vol.~154, pp. 2499--2510, 2006.


\bibitem{laih06a}
T. LAIHONEN: Optimal $t$-edge-robust $r$-identifying codes in the king lattice, {\it Graphs and Combinatorics}, Vol.~22, pp. 487--496, 2006.

\bibitem{laih05a}
T. LAIHONEN: On edge-robust $(1,\leq\ell)$-identifying codes in binary Hamming spaces, {\it International Journal of Pure and Applied Mathematics}, Vol.~36, pp. 87--102, 2007.

\bibitem{laih08}
T. LAIHONEN: On cages admitting identifying codes, {\it European Journal of Combinatorics}, Vol.~29, pp. 737--741, 2008.

\bibitem{laih16}
T. LAIHONEN: The metric dimension for resolving several objects, {\it Information Processing Letters}, Vol.~116(11), pp. 694--700, 2016.

\bibitem{laih17}
T. LAIHONEN: Information retrieval and the average number of input clues, {\it Advances in Mathematics of Communications}, Vol.~11, pp. 203--223, 2017.

\bibitem{laih19q}
T. LAIHONEN: On $t$-revealing codes in binary Hamming spaces, {\it Information and Computation}, Vol. 268, 104455, 11 pages, 2019.

\bibitem{laih08b}
T. LAIHONEN and J. MONCEL: On graphs admitting codes identifying sets of vertices, {\it Australasian Journal of Combinatorics}, Vol.~41, pp. 81--91, 2008.

\bibitem{laih01a}
T. LAIHONEN and S. RANTO: Codes identifying sets of vertices, {\it Lecture Notes in Computer Science}, No. 2227, pp. 82--91, Springer-Verlag, 2001.

\bibitem{laih02b}
T. LAIHONEN and S. RANTO: Families of optimal codes for strong identification, {\it Discrete Applied Mathematics}, Vol.~121, pp. 203--213, 2002.

\bibitem{laih07}
T. LAIHONEN and S. RANTO: Codes identifying sets of binary words with large radii, {\it Proceedings of Workshop on Coding and Cryptography 2007}, Versailles, France, pp. 215--224, 2007.

\bibitem{laks00}
K. B. LAKSHMANAN, D. J. ROSENKRATZ and S. S. RAVI: Alarm placement in systems with fault propagation, {\it Theoretical Computer Science}, Vol.~243, pp. 269--288, 2000.

\bibitem{lane06}
S. M. LANE: Trees with unique minimum locating-dominating sets, {\it Master's Thesis, East Tennessee State University}, USA, 72 pages, 2006.

\bibitem{li08}
M. S. LI, E. F. SHAN and M. J. GAO: Bounds for fault-tolerant locating-dominating sets, {\it Journal of Shanghai University. Natural Science}, Vol.~14(6), pp. 611--616, 2008 (in Chinese).

\bibitem{lobs20}
A. LOBSTEIN, O. HUDRY and I. CHARON: Locating-Domination and Identification, {\it Topics in Domination in Graphs}, T. Haynes, S. Hedetniemi \& M. Henning, Eds., pp. 251--299, Springer, 2020.

\bibitem{lu19}
M. LU, J. XU and Y. ZHANG: Identifying codes in the direct product of a complete graph and some special graphs, {\it Discrete Applied Mathematics}, Vol.~254, pp. 175--182, 2019.

\bibitem{mcco09}
J. McCOY and M. A. HENNING: Locating and paired-dominating sets in graphs, {\it Discrete Applied Mathematics}, Vol.~157, pp. 3268--3280, 2009.

\bibitem{mcin19}
F. MC~INERNEY: Domination and identification games in graphs, {\it Th\`ese de Doctorat}, Universit\'e C\^ote d'Azur, France, xii+157 pages, July 2019.

\bibitem{madd21}
S. MADDAH, M. GHORBANI and M. DEHMER: New results of identifying codes in product graphs, {\it Applied Mathematics and Computation}, Vol. 410, 126438, 7 pages, 2021.

\bibitem{manu11}
P. MANUEL: Locating and liar domination of circulant networks, {\it Ars Combinatoria}, Vol.~101, pp. 309--320, 2011.

\bibitem{mart10}
R. MARTIN and B. STANTON: Lower bounds for identifying codes in some infinite grids, {\it Electronic Journal of Combinatorics}, Vol.~17(1), R122, 2010.\\
http://www.combinatorics.org

\bibitem{mila13a}
M. MILANI\u{C} and A. I. TOMESCU: Set graphs. I. Hereditarily finite sets and extensional acyclic orientations, {\it Discrete Applied Mathematics}, Vol.~161, pp. 677--690, 2013.

\bibitem{mila13b}
M. MILANI\u{C}, R. RIZZI and A. I. TOMESCU: Set graphs. II. Complexity of set graph recognition and similar problems, {\it Theoretical Computer Science}, Vol.~547, pp. 70--81, 2014.

\bibitem{mill17}
M. MILLER, R. S. RAJAN, R. JAYAGOPAL, I. RAJASINGH and P. MA\-NUEL: A note on the locating-total domination in graphs, {\it Discussiones Mathematicae Graph Theory}, Vol. 37, pp. 745--754, 2017.

\bibitem{mimoC22}
M. MIMOUNI, N. IKHLEF-ESCHOUF and M. ZAMIME: On connected 3-$\gamma_L$-dot-critical graphs, {\it Bulletin of the Iranian Mathematical Society}, to appear.

\bibitem{mojd22}
D. A. MOJDEH: On the conjectures of neighbor locating coloring of graphs, {\it Theoretical Computer Science}, Vol. 922, pp. 300--307, 2022.

\bibitem{monc05c}
J. MONCEL: Codes identifiants dans les graphes, {\it Th\`ese de Doctorat}, Universit\'e de Grenoble, France, 165 pages, June 2005.

\bibitem{monc05d}
J. MONCEL: Codes identifying vertices in graphs, {\it Proceedings of the 7th International Colloquium on Graph Theory}, Giens, France, 2005.

\bibitem{monc05a}
J. MONCEL: Monotonicity of the minimum cardinality of an identifying code in the hypercube, {\it Discrete Applied Mathematics}, Vol.~154, pp. 898--899, 2006.

\bibitem{monc06b}
J. MONCEL: On graphs on $n$ vertices having an identifying code of cardinality $\lceil \log_2 (n+1)\rceil$, {\it Discrete Applied Mathematics}, Vol.~154, pp. 2032--2039, 2006.

\bibitem{monc06a}
J. MONCEL: Constructing codes identifying sets of vertices, {\it Designs, Codes and Cryptography}, Vol.~41, pp. 23--31, 2006.

\bibitem{monc04}
J. MONCEL and M. RUSZINK\'O: Codes identifiant des ensembles de sommets, {\it Les Cahiers du Laboratoire Leibniz}, No.~114, pp. 65--67, 2004.

\bibitem{more85}
B. M. E. MORET and H. D. SHAPIRO: On minimizing a set of tests, {\it SIAM Journal on Scientific and Statistical Computing}, Vol.~6, pp. 983--1003, 1985.

\bibitem{mull09}
T. M\"{U}LLER and J. S. SERENI: Identifying and locating-dominating codes in (random) geometric networks, {\it Combinatorics, Probability and Computing}, Vol.~18, pp. 925--952, 2009.

\bibitem{murt19}
M. MURTAZA, M. FAZIL and I. JAVAID: Locating-dominating sets of functigraphs, {\it Theoretical Computer Science}, Vol. 799, pp. 115--123, 2019.

\bibitem{murt2020}
M. MURTAZA, I. JAVAID and M. FAZIL: Covering codes of a graph associated to a finite vector space, {\it Ukra\"{i}nskii Matematicheskii Zhurnal}, Vol. 72(7), pp. 952--959, 2020. Reprinted in {\it Ukrainian Mathematical Journal}, Vol. 72(7), pp. 1108--1117, 2020.

\bibitem{muth12b}
S. MUTHAMMAI and N. MEENAL: Co-isolated locating domination number for  some  standard  graphs, {\it National Conference on  Applications of Mathematics \& Computer Science (NCAMCS-2012)}, S.D.N.B  Vaishnav College for Women (Autonomous), Chennai (India), pp.  60--61, February 2012.

\bibitem{muth12}
S. MUTHAMMAI and N. MEENAL: Co-isolated locating domination number of a  graph, {\it Proceedings of the UGC Sponsored National Seminar on  Applications  in  Graph Theory}, Seethalakshmi  Ramaswamy  College (Autonomous), Tiruchirappalli (India), pp. 7--9, December 2012.

\bibitem{muth15}
S. MUTHAMMAI and N. MEENAL: Co-isolated locating domination number for the complement of a doubly connected graph, {\it International Journal of Mathematics and Scientific Computing}, Vol.~5(1), pp. 57--59, 2015.

\bibitem{niep15}
L. NIEPEL: Locating-paired-dominating sets in square grids, {\it Discrete Mathematics}, Vol.~338, pp. 1699--1705, 2015.

\bibitem{nika20}
R. NIKANDISH, O. KHANI~NASAB and E. DODONGE: Minimum identifying codes in some graphs differing by matchings, {\it Discrete Mathematics, Algorithms and Applications}, Vol. 12(3), 2050046, 8 pages, 2020.

\bibitem{ning16}
W. NING, M. LU and J. GUO: Bounds on the differentiating-total domination number of a tree, {\it Discrete Applied Mathematics}, Vol.~200, pp. 153--160, 2016.

\bibitem{ning17}
W. NING, M. LU and J. GUO: Locating and differentiating-total dominating sets in unicyclic graphs, {\it Ars Combinatoria}, Vol.~132, pp. 241--255, 2017.

\bibitem{ning19}
W. NING, M. LU and K. WANG: Bounding the locating-total domination number of a tree in terms of its annihilation number, {\it Discussiones Mathematicae Graph Theory}, Vol. 39, pp. 31--40, 2019.

\bibitem{obat03}
K. OBATA: On identifying codes in lattices, {\it Preprint}, December 2003.\\
http://www.kenjioba.net/images/Identifying.pdf

\bibitem{omam14}
B. N. OMAMALIN, S. R. CANOY, Jr., and H. M. RARA: Locating total dominating sets in the join, corona and composition of graphs, {\it Applied Mathematical Sciences (Ruse)}, Vol.~8(45--48), pp. 2363--2374, 2014.

\bibitem{omam14b}
B. N. OMAMALIN, S. R. CANOY, Jr., and H. M. RARA: Differentiating total domination in graphs: Revisited, {\it International Journal of Mathematical Analysis}, Vol.~8, pp. 2789--2798, 2014.

\bibitem{pand17}
B. S. PANDA and A. PANDEY: Algorithmic aspects of open neighbourhood location-domination in graphs, {\it Discrete Applied Mathematics}, Vol.~216(1), pp. 290--306, 2017.

\bibitem{pand15}
A. PANDEY: Open neighborhood locating-dominating set in graphs: Complexity and algorithms, {\it Proceedings of the 14th International Conference on Information Technology (ICIT 2015)}, Bhubaneswar, India, pp. 1-6, 2015.

\bibitem{pari18}
G. PARIS: Resolution of some optimisation problems on graphs and combinatorial games, {\it Th\`ese de Doctorat}, Universit\'e Claude Bernard Lyon 1, France, 142 pages, October 2018.

\bibitem{parr12}
A. PARREAU: Probl\`emes d'identification dans les graphes, {\it Th\`ese de Doctorat}, Universit\'e de Grenoble, France, 214 pages, July 2012.

\bibitem{past11}
M. PASTORI: Les codes identifiants ou comment sauver le Palais des flammes?, {\it D\'ecouverte}, Vol.~369, pp. 56--59, 2010.

\bibitem{payn80}
R. W. PAYNE and D. A. PREECE: Identification keys and diagnostic tables: a review, {\it Journal of the Royal Statistical Society}, Ser. A, Vol.~143, pp. 253--292, 1980.

\bibitem{pela10}
I. M. PELAYO: Locating domination in graphs, {\it Abstracts of the 8th French Combinatorial Conference}, Orsay, France, No.~150, 2010.

\bibitem{pelt10}
M. PELTO: New bounds for $(r,\leq 2)$-identifying codes in the infinite king grid, {\it Cryptography and Communications}, Vol.~2, pp. 41--47, 2010.

\bibitem{pelt11}
M. PELTO: On locating-dominating codes for locating large numbers of vertices in the infinite king grid, {\it Australasian Journal of Combinatorics}, Vol.~50, pp. 127--139, 2011.

\bibitem{pelt12}
M. PELTO: On ($r, \leq 2$)-locating-dominating codes in the infinite king grid, {\it Advances in Mathematics of Communications}, Vol.~6, pp. 27--38, 2012.

\bibitem{pelt12b}
M. PELTO: On identifying and locating-dominating codes in the infinite king grid, {\it Ph. D. Thesis}, University of Turku, Finland, 133 pages, 2012.

\bibitem{pelt13d}
M. PELTO: Optimal ($r, \leq 3$)-locating-dominating codes in the infinite king grid, {\it Discrete Applied Mathematics}, Vol.~161, pp. 2597--2603, 2013.

\bibitem{pelt13e}
M. PELTO: Optimal identifying codes in the infinite $3$-dimensional king grid, {\it European Journal of Combinatorics}, Vol. 36, pp. 641--659, 2014.

\bibitem{pelt13}
M. PELTO: Maximum difference about the size of optimal identifying codes in graphs differing by one vertex, {\it Discrete Mathematics \& Theoretical Computer Science}, Vol. 17(1), pp. 339--356, 2015.

\bibitem{pelt13b}
M. PELTO: On locating-dominating codes in the infinite king grid, {\it Ars Combinatoria}, Vol.~124, pp. 353--363, 2016.

\bibitem{pelto17z}
M. PELTO: The number of completely different optimal identifying codes in the infinite square grid, {\it Discrete Applied Mathematics}, Vol.~233, pp. 143--158,  2017.

\bibitem{pirz14}
S. PIRZADA, R. RAJA and S. REDMOND: Locating sets and numbers of graphs associated to commutative rings, {\it Journal of Algebra and Its Applications}, Vol.~13(7), 1450047, 18 pages, 2014.

\bibitem{pu2013}
L. Q. PU and Y. L. CHAI: Bounds of $r$-identifying and $r$-locating-dominating codes in the Kronecker product graph of $cy_n$ and $\bar{k}_2$, {\it Journal of Zhengzhou University. Natural Science}, Vol.~45, pp10--12, 2013 (in Chinese).

\bibitem{rad18}
N. J. RAD and H. RAHBANI: Bounds on the locating-domination number and differentiating-total domination number in trees, {\it Discussiones Mathematicae Graph Theory}, Vol.~38, pp. 455--462, 2018.

\bibitem{rahb19}
H. RAHBANI, N. J. RAD and S. M. MIRREZAEI: Bounds on the identifying codes in trees, {\it Graphs and Combinatorics}, Vol.~35, pp. 599--609, 2019.

\bibitem{rahb19q}
H. RAHBANI, N. J. RAD and M. R. SADEGHI: A note on the complexity of locating-total domination in graphs, {\it Theoretical Computer Science}, Vol.~799, pp. 32--39, 2019.

\bibitem{rahb21R}
H. RAHBANI, A. TAHERIFAR and N. J. RAD: Trees with no locating Roman domination critical vertices, {\it Iranian Journal of Science and Technology, Transaction A}, Vol. 45(2), pp. 585--592, 2021.

\bibitem{raja16}
R. RAJA, S. PIRZADA and S. REDMOND: On locating numbers and codes of zero divisor graphs associated with commutative rings, {\it Journal of Algebra and Its Applications}, Vol.~15(1), 1650014, 22 pages, 2016.

\bibitem{raja19w}
G. RAJASEKAR and K. NAGARAJAN: Location domination number of line graph, {\it Journal of Discrete Mathematical Sciences and Cryptography}, Vol. 22(5), pp. 777--786, 2019.

\bibitem{rajas20}
I. RAJASINGH, R. JAYAGOPAL and R. S. RAJAN: Domination parameters in hypertrees and sibling trees, {\it Discrete Applied Mathematics}, Vol. 280, pp. 237--245, 2020.

\bibitem{rall84a}
D. F. RALL and P. J. SLATER: On location-domination numbers for certain classes of graphs, {\it Congressus Numerantium}, Vol.~45, pp. 97--106, 1984.

\bibitem{rall12}
D. F. RALL and K. WASH: Identifying codes of the direct product of two cliques, {\it European Journal of Combinatorics}, Vol.~36, pp. 159--171, 2014.

\bibitem{rall17z}
D. F. RALL and K. WASH: On minimum identifying codes in some Cartesian product graphs, {\it Graphs and Combinatorics}, Vol.~33, pp. 1037--1053, 2017.

\bibitem{rant04a}
S. RANTO: Optimal linear identifying codes, {\it IEEE Transactions on Information Theory}, Vol. IT-49, pp. 1544--1547, 2003.

\bibitem{rant07}
S. RANTO: Identifying and locating-dominating codes in binary Hamming spaces, {\it Ph. D. Thesis}, University of Turku, Finland, 95 pages, 2007.

\bibitem{rant11}
S. RANTO: On binary linear $r$-identifying codes, {\it Designs, Codes and Cryptography}, Vol.~60, pp. 81--89, 2011.

\bibitem{rant02a}
S. RANTO, I. HONKALA and T. LAIHONEN: Two families of optimal identifying codes in binary Hamming spaces, {\it IEEE Transactions on Information Theory}, Vol. IT-48, pp. 1200--1203, 2002.

\bibitem{rao93}
N. S. V. RAO: Computational complexity issues in operative diagnosis of graph-based systems, {\it IEEE Transactions on Computers}, Vol.~42, pp. 447--457, 1993.

\bibitem{rasp12}
A. RASPAUD and L. D. TONG: The minimum identifying code graphs, {\it Discrete Applied Mathematics}, Vol.~160, pp. 1385--1389, 2012.

\bibitem{ray04a}
S. RAY, D. STAROBINSKI, A. TRACHTENBERG and R. UNGRANGSI: Robust location detection with sensor networks, {\it IEEE Journal on Selected Areas in Communications}, Vol. 22(6), pp. 1016--1025, 2004.

\bibitem{ray03a}
S. RAY, R. UNGRANGSI, F. DE~PELLEGRINI, A. TRACHTENBERG and D. STAROBINSKI: Robust location detection in emergency sensor networks, {\it Proceedings of INFOCOM 2003}, San Francisco, USA, pp. 1044--1053, April 2003.

\bibitem{raza21}
H. RAZA: Computing open locating-dominating number of some rotationally-symmetric graphs, {\it Mathematics}, Vol. 9(12), 2021.

\bibitem{raza18e}
H. RAZA, S. HAYAT and X. F. PAN: Binary locating-dominating sets in rotationally-symmetric convex polytopes, {\it Symmetry}, Vol. 10(12), 2018.

\bibitem{robe07}
D. L. ROBERTS and F. S. ROBERTS: Locating sensors in paths and cycles: the case of $2$-identifying codes, {\it European Journal of Combinatorics}, Vol.~29, pp. 72--82, 2008.

\bibitem{rode09}
M. L. RODEN and P. J. SLATER: Liar's domination in graphs, {\it Discrete Mathematics}, Vol.~309, pp. 5884--5890, 2009.

\bibitem{rooz17}
M. ROOZBAYANI and H. R. MAIMANI: Identifying codes and watching systems in Kneser graphs, {\it Discrete Mathematics, Algorithms and Applications}, Vol.~9, 1750007, 2017.

\bibitem{rooz14}
M. ROOZBAYANI, H. R. MAIMANI and A. TEHRANIAN: Watching systems of triangular graphs, {\it Transactions on Combinatorics}, Vol. 3, pp. 51--57, 2014.

\bibitem{rose03a}
P. ROSENDAHL: On the identification of vertices using cycles, {\it Electronic Journal of Combinatorics}, Vol.~10(1), R7, 2003.\\
http://www.combinatorics.org

\bibitem{rose04a}
P. ROSENDAHL: On the identification problems in products of cycles, {\it Discrete Mathematics}, Vol.~275, pp. 277--288, 2004.

\bibitem{savi18}
A. Lj. SAVI\'C, Z. Lj. MAKSIMOVI\'C and M. S. BOGDANOVI\'C: The open-locating-dominating number of some convex polytopes, {\it Filomat}, Vol. 32(2), pp. 635--642, 2018.

\bibitem{seag12}
S. M. SEAGER: Locating a robber on a graph, {\it Discrete Mathematics}, Vol. 312, pp. 3265--3269, 2012.

\bibitem{seag13}
S. M. SEAGER: A sequential locating game on graphs, {\it Ars Combinatoria}, Vol. 110, pp. 45--54, 2013.

\bibitem{seag14}
S. M. SEAGER: Locating a backtracking robber on a tree, {\it Theoretical Computer Science}, Vol. 539, pp. 28--37, 2014.

\bibitem{seo18}
S. J. SEO: Open-locating-dominating sets in the infinite king grid, {\it Journal of Combinatorial Mathematics and Combinatorial Computing}, Vol. 104, pp. 31--47, 2018.

\bibitem{seo21c}
S. J. SEO: Fault-tolerant detectors for distinguishing sets in cubic graphs, {\it Discrete Applied Mathematics}, Vol. 293, pp. 25--33, 2021.

\bibitem{seo10}
S. J. SEO and P. J. SLATER: Open neighborhood locating-dominating sets, {\it Australasian Journal of Combinatorics}, Vol.~46, pp. 109--119, 2010.

\bibitem{seo11}
S. J. SEO and P. J. SLATER: Open neighborhood locating-dominating in trees, {\it Discrete Applied Mathematics}, Vol.~159, pp. 484--489, 2011.

\bibitem{seo11b}
S. J. SEO and P. J. SLATER: Open neighborhood locating-domination for infinite cylinders, {\it Proceedings of ACM SE 11}, Kennesaw, USA, pp. 334-335, 2011.

\bibitem{seo12a}
S. J. SEO and P. J. SLATER: Graphical parameters for classes of tumbling block graphs, {\it Congressus Numerantium}, Vol.~213, pp. 155--168, 2012.

\bibitem{seo12}
S. J. SEO and P. J. SLATER: Open neighborhood locating-domination for grid-like graphs, {\it Bulletin of the Institute of Combinatorics and its Applications}, Vol.~65, pp. 89--100, 2012.

\bibitem{seo13}
S. J. SEO and P. J. SLATER: Open locating-dominating interpolation for trees, {\it Congressus Numerantium}, Vol.~215, pp. 145--152, 2013.

\bibitem{seo14}
S. J. SEO and P. J. SLATER: OLD trees with maximum degree three, {\it Utilitas Mathematica}, Vol.~94, pp. 361--380, 2014.

\bibitem{seo15}
S. J. SEO and P. J. SLATER: Fault tolerant detectors for distinguishing sets in graphs, {\it Discussiones Mathematicae Graph Theory}, Vol.~35, pp. 797--818, 2015.

\bibitem{seo17z}
S. J. SEO and P. J. SLATER: Open-independent, open-locating-dominating sets, {\it Electronic Journal of Graph Theory and Applications}, Vol.~5, pp. 179--193, 2017.

\bibitem{sewe10}
J. L. SEWELL and P. J. SLATER: Locating mobile intruders using dominating sets, {\it Journal of Combinator2050046ial Mathematics and Combinatorial Computing}, Vol.~74, pp. 253--267, 2010.

\bibitem{sewe14}
J. L. SEWELL and P. J. SLATER: A sharp lower bound for locating-dominating sets in trees, {\it Australasian Journal of Combinatorics}, Vol.~60, pp. 136--149, 2014.

\bibitem{sham22B}
A. SHAMINEJAD and E. VATANDOOST: The identifying code number and functigraphs, {\it Journal of Algebraic Systems}, Vol. 10, pp. 155--166, 2022.

\bibitem{sham22A}
A. SHAMINEJAD, E. VATANDOOST and K. MIRASHEH: The identifying code number and Mycielski's construction of graphs, {\it Transactions on Combinatorics}, Vol. 11, pp. 309--316, 2022.

\bibitem{shinC22}
N. V. SHINDE, S. A. MANE and B. N. WAPHARE: Identifying codes in the direct product of a path and a complete graph, {\it Discussiones Mathematicae Graph Theory}, Vol. 43(2), pp. 463--486, 2023.

\bibitem{shin20k}
N. V. SHINDE and B. N. WAPHARE: Improved upper bounds for identifying codes in $n$-dimensional $q$-ary cubes, {\it International Journal of Applied and Computational Mathematics}, Vol. 6(2), Paper No. 43, 11 pages, 2020.

\bibitem{simi17}
A. SIMI\'C, M. BOGDANOVI\'C and J. MILOSEVI\'C: The binary locating-dominating number of some convex polytopes, {\it Ars Mathematica Contemporanea}, Vol. 13, pp. 367--377, 2017.

\bibitem{skag07}
R. D. SKAGGS: Identifying vertices in graphs and digraphs, {\it Ph. D. Thesis}, University of South Africa, South Africa, 88 pages, 2007.

\bibitem{slat75a}
P. J. SLATER: Leaves of trees, {\it Congressus Numerantium}, Vol.~14, pp. 549--559, 1975.

\bibitem{slat83}
P. J. SLATER: Domination and location in graphs, {\it National University of Singapore}, Research Report No.~93, April 1983.

\bibitem{slat87a}
P. J. SLATER: Domination and location in acyclic graphs, {\it Networks}, Vol.~17, pp. 55--64, 1987.

\bibitem{slat88a}
P. J. SLATER: Dominating and reference sets in a graph, {\it Journal of Mathematical and Physical Sciences}, Vol.~22, pp. 445--455, 1988.

\bibitem{slat95a}
P. J. SLATER: Locating dominating sets and locating-dominating sets, {\it Graph Theory, Combinatorics, and Applications: Proceedings of the 7th Quadrennial International Conference on the Theory and Applications of Graphs}, Vol.~2, pp. 1073--1079, Wiley, 1995.

\bibitem{slat02a}
P. J. SLATER: Fault-tolerant locating-dominating sets, {\it Discrete Mathematics}, Vol. 249, pp. 179--189, 2002.

\bibitem{slat09}
P. J. SLATER: Liar's domination, {\it Networks}, Vol. 54, pp. 70--74, 2009.

\bibitem{slat13}
P. J. SLATER: A framework for faults in detectors within network monitoring systems, {\it WSEAS Transactions on Mathematics}, Vol.~12, pp. 911--916, 2013.

\bibitem{slat14p}
P. J. SLATER and J. L. SEWELL: A sharp lower bound for locating-dominating sets in trees, {\it Australasian Journal of Combinatorics}, Vol. 60, pp. 136--149, 2014.

\bibitem{slat18}
P. J. SLATER and J. L. SEWELL: Independent locating-dominating sets and identifying codes in graphs, {\it Journal of Combinatorial Mathematics and Combinatorial Computing}, Vol. 104, pp. 261--272, 2018.

\bibitem{song22}
S. J. SONG, X. NING and P. CHENG: Locating and identifying codes in dihedral graphs, {\it Applied Mathematics and Computation}, Vol.~416, Paper No. 126752, 2022.

\bibitem{song21}
S. J. SONG, W. ZHANG and C. XU: Locating and identifying codes in circulant graphs, {\it Discrete Dynamics in Nature and Society}, Vol. 2021, Article ID 4056910, 9 pages, 2021.

\bibitem{stan11b}
B. STANTON: Improved bounds for $r$-identifying codes of the hex grid, {\it SIAM Journal on Discrete Mathematics}, Vol.~25, pp. 159--169, 2011.

\bibitem{stan11}
B. STANTON: On vertex identifying codes for infinite lattices, {\it Ph. D. Thesis}, Iowa State University, USA, 94 pages, 2011.\\
http://orion.math.iastate.edu/rymartin/students/StantonB$_{-}$ PhD$_{-}$S11.pdf

\bibitem{stan12}
B. STANTON: Vertex identifying codes for the $n$-dimensional lattice, {\it Australasian Journal of Combinatorics}, Vol.~53, pp. 299--307, 2012.

\bibitem{stew84}
L. K. STEWART: Minimum locating dominating sets in cographs, {\it Unpublished manuscript}, 1984.

\bibitem{sumn73}
 D. P. SUMNER: Point determination in graphs, {\it Discrete Mathematics}, Vol.~5, pp. 179--187, 1973.

\bibitem{suom07}
J. SUOMELA: Approximability of identifying codes and locating-dominating codes, {\it Information Processing Letters}, Vol. 103, pp. 28--33, 2007.

\bibitem{swei19k}
D. B. SWEIGART: Optimization approaches for open-locating dominating sets, {\it Ph.D. Thesis}, The College of William and Mary, Virginia, USA, 137 pages, 2019.

\bibitem{swei18}
B. SWEIGART and R. KINCAID: Maximum covering formulation for open locating dominating sets, {\it Operations Research Proceedings 2016}, pp. 259--264, 2018.

\bibitem{swei14}
B. SWEIGART, J. PRESNELL and R. KINCAID: An integer program for open locating dominating sets and its results on the hexagon-triangle infinite grid and other graphs, {\it 2014 Systems and Information Engineering Design Symposium (SIEDS), Charlottesville, USA}, pp. 29--32, 2014.

\bibitem{thul07}
K. THULASIRAMAN, M. XU, Y. XIAO and X. D. HU: Vertex identifying codes for fault isolation in communication networks, {\it Proceedings of the International Conference on Discrete Mathematics and Applications (ICDM 2006)}, Bangalore, India, 2006.

\bibitem{tong14}
L. D. TONG: Automorphisms of neighborhood sequence of a graph, {\it Proceedings of Bordeaux Graph Workshop}, Bordeaux, France, pp. 133--134, 2014.

\bibitem{ungr03}
R. UNGRANGSI: Location detection in emergency sensor networks using robust identifying codes, {\it M.S. thesis}, Boston University, Boston, USA, 116 pages, 2003.

\bibitem{ungr04}
R. UNGRANGSI, A. TRACHTENBERG and D. STAROBINSKI: An implementation of indoor location detection systems based on identifying codes, {\it Lecture Notes in Computer Science}, No. 3283, pp. 175--189, Springer-Verlag, 2004.

\bibitem{vali12}
P. VALICOV: Probl\`emes de placement, de coloration et d'identification, {\it Th\`ese de Doctorat}, Universit\'e de Bordeaux~1, France, 110 pages, 2012.

\bibitem{vand18}
M. VANDERMEER: Codes identifiants de graphes, {\it M\'emoire de Master}, Universit\'e de Li\`ege (D\'epartement de Math\'e\-matiques), Belgique, 82 pages, 2018.

\bibitem{wash14}
K. WASH: Identifying codes and domination in the product of graphs, {\it Ph. D. Thesis}, Clemson University, USA, 63 pages, 2014.

\bibitem{xiao06}
Y. XIAO, C. HADJICOSTIS and K. THULASIRAMAN: The $d$-identifying codes problem for vertex identification in graphs: probabilistic analysis and an approximation algorithm, {\it Proceedings of COCOON 2006, 12th Annual International Computing and Combinatorics Conference}, Taipei, Taiwan, pp. 284--298, 2006.

\bibitem{xing14}
H. XING and M. Y. SOHN: Bounds on locating-total domination number of the Cartesian product of cycles, {\it Ars Combinatoria}, Vol.~113A, pp. 139--146, 2014.

\bibitem{xing15}
H. XING and M. Y. SOHN: Bounds on locating total domination number of the Cartesian product of cycles and paths, {\it Information Processing Letters}, Vol.~115(12), pp. 950--956, 2015.

\bibitem{xu07}
M. XU, K. THULASIRAMAN and X. D. HU: Identifying codes of cycles with odd orders, {\it European Journal of Combinatorics}, Vol. 29, pp. 1717--1720, 2008.

\bibitem{xu07b}
Y.-C. XU and R.-B. XIAO: Solving the identifying code problem by a genetic algorithm, {\it IEEE Transactions on Systems, Man and Cybernetics}, Part A, Vol. 37(1), pp. 41--46, 2007.

\bibitem{xu07c}
Y.-C. XU and R.-B. XIAO: Identifying code for directed graph, {\it Proceedings of Eighth ACIS International Conference on Software Engineering, Artificial Intelligence, Networking, and Parallel/Distributed Computing (SNPD 2007)}, Vol. 2, pp. 97--101, 2007.

\bibitem{yaak12}
E. YAAKOBI and J. BRUCK: On the uncertainty of information retrieval in associative memories, {\it Proceedings of the 2012 IEEE International Symposium on Information Theory}, pp. 106--110, 2012.

\bibitem{yaak18}
E. YAAKOBI and J. BRUCK: On the uncertainty of information retrieval in associative memories, {\it IEEE Transactions on Information Theory}, Vol. IT-65(4), pp. 2155--2165, 2018.

\bibitem{yao17}
J. YAO, X. YU, G. WANG and C. XU: Neighbor sum distinguishing total coloring of $2$-degenerate graphs, {\it Journal of Combinatorial Optimization}, Vol. 34, pp. 64--70, 2017.

\bibitem{zakr98}
L. ZAKREVSKI and M. G. KARPOVSKY: Fault-tolerant message routing for multiprocessors, {\it Parallel and Distributed Processing}, J. Rolim, Ed., pp. 714--731, Springer, 1998.

\bibitem{zakr99a}
L. ZAKREVSKI and M. G. KARPOVSKY: Fault-tolerant message routing in computer networks, {\it Proceedings of International Conference on Parallel and Distributed Processing Techniques and Applications}, pp. 2279--2287, 1999.

\bibitem{zhan05}
Z. ZHANG, X. CHEN, J. LI, B. YAO, X. LU and J. WANG: On adjacent-vertex-distinguishing total coloring of graphs, {\it Science in China, Ser. A: Mathematics}, Vol.~48, pp. 289--299, 2005.

\end{thebibliography}
\end{document}
